---
title: "allcode.rmd"
author: "Anisha Nagpal"
date: "November 24, 2019"
output: html_document
---
This document contains all the code to conver the data and upload to REDCap. 
Before running this document, change x=read.csv("LOCATION OF FILE TO READ IN", ......)
At the bottom of the document, change write.csv to the appropriate document name and location to save the new csv file for upload to REDCap

```{r institute, include=FALSE}
library(plyr)
library(readr)
library(dplyr)
library(tidyverse)
library(lubridate)
x=read.csv("~/Zero TB in Kids/ztbtk_data/Lower_TCV_Main.csv",stringsAsFactors = FALSE, na.strings=TRUE)
##Insitute variable renaming
##need to write this in based on what you see in the document
x$institute[x$institute=="LTCV"]<-1
x$institute[x$institute=="LowerTCV"]<-1
x$institute[x$institute=="GTCV"]<-3
x$institute[x$institute=="TCV GOPUR"]<-3
x$institute[x$institute=="LTCV"]<-1
x$institute[x$institute=="LTCV"]<-1
x$institute[x$institute=="STSP"]<-10
x$institute[x$institute=="STCV"]<-4
```

```{r age}
x$age[x$age=="NA"]<-""
```

```{r sex}
x$sex[grepl("^m", x$sex, ignore.case = TRUE)]<-1
x$sex[grepl("^f", x$sex, ignore.case = TRUE)]<-2
x$sex[x$sex==""]<-9
x$sex[grepl("^na", x$sex, ignore.case = TRUE)]<-99
x$class_section[x$class_section=="NA"]<-""
```

```{r main TB Dorm}
x$dorm_[!grepl("^b|^h|^g|^s|^d",x$dorm,ignore.case=TRUE)] <-""
x$dorm[grepl("^k",x$dorm,ignore.case=TRUE)] <-""
x$dorm[grepl("^H-",x$dorm,ignore.case=TRUE)] <- 1
x$dorm[grepl("^H",x$dorm,ignore.case=TRUE)] <- 1
x$dorm[grepl("^G",x$dorm,ignore.case=TRUE)] <- 3
x$dorm[grepl("^B",x$dorm,ignore.case=TRUE)] <- 2
x$dorm[grepl("^sta", x$dorm, ignore.case = TRUE)]<-5
x$dorm[grepl("^da", x$dorm, ignore.case = TRUE)]<-4


x$dorm[x$dorm==""]<-9
x$dorm[x$dorm=="NA"]<-99


x$enroll_date[x$enroll_date=="NA"]<-""

```


```{r occupation}

x$occupation[grepl("^stu",x$occupation,ignore.case=TRUE)] <- 1
x$occupation[grepl("^tea",x$occupation,ignore.case=TRUE)] <- 2
x$occupation[grepl("^heal",x$occupation,ignore.case=TRUE)] <-3
x$occupation[grepl("^off",x$occupation,ignore.case=TRUE)] <-4
x$occupation[grepl("moth",x$occupation,ignore.case=TRUE)] <- 5
x$occupation[grepl("^mon",x$occupation,ignore.case=TRUE)] <- 6
x$occupation[grepl("^nun",x$occupation,ignore.case=TRUE)] <- 7
x$occupation[grepl("^coo",x$occupation,ignore.case=TRUE)] <- 8
x$occupation[grepl("^dri",x$occupation,ignore.case=TRUE)] <- 9
x$occupation[grepl("fath",x$occupation,ignore.case=TRUE)] <- 10
x$occupation[grepl("other",x$occupation,ignore.case=TRUE)] <- 11
x$occupation[grepl("^na",x$occupation,ignore.case=TRUE)] <- 99
x$occupation[x$occupation==""]<-999
```

```{r Country}
x$birth_place[!grepl('^IND|^TIB|^NEP|^BHU|^US|^CAN', x$birth_place,ignore.case=TRUE)] <- 5
x$birth_place[grepl("^ind",x$birth_place,ignore.case=TRUE)] <- 1
x$birth_place[grepl("^tib",x$birth_place,ignore.case=TRUE)] <- 2
x$birth_place[grepl("^nep",x$birth_place,ignore.case=TRUE)] <- 3
x$birth_place[grepl("^bhu",x$birth_place,ignore.case=TRUE)] <- 4
x$birth_place[grepl("^usa",x$birth_place,ignore.case=TRUE)] <- 5
x$birth_place[grepl("^can",x$birth_place,ignore.case=TRUE)] <- 6
x$birth_place[x$birth_place==""]<-9
x$birth_place[grepl("^na",x$birth_place,ignore.case=TRUE)] <- 99

x$arrivealyear_fromtibet[grepl("^na",x$arrivealyear_fromtibet,ignore.case=TRUE)] <- ""
x$ethnicity[grepl("^na",x$ethnicity,ignore.case=TRUE)] <- ""
```

```{r run}
x$address_settlement_city[grepl("^na",x$address_settlement_city,ignore.case=TRUE)] <- ""
x$weight_kg[grepl("^na",x$weight_kg,ignore.case=TRUE)] <- ""

```

############################################################
###ALL CODE ABOVE MUST BE RUN FOR EACH SHEET
############################################################


##MAIN DATABASE tb INVESTIGATION CODE
```{r prev tb}
x$prev_tb[grepl("^no",x$prev_tb,ignore.case=TRUE)] <- 0
x$prev_tb[grepl("^yes",x$prev_tb,ignore.case=TRUE)] <- 1
x$prev_tb[x$prev_tb==""]<-9
x$prev_tb[grepl("^na",x$prev_tb,ignore.case=TRUE)] <- 99
```

```{r year and site of previous TB}
x$prevtb_year[grepl("^na",x$prevtb_year,ignore.case=TRUE)] <-""
x$prevtb_site[grepl("^na",x$prevtb_site,ignore.case=TRUE)] <-""
```


```{r prev tb type}
x$prevtb_type[grepl("^non",x$prevtb_type,ignore.case=TRUE)] <- 0
x$prevtb_type[grepl("^mdr",x$prevtb_type,ignore.case=TRUE)] <- 1
x$prevtb_type[x$prevtb_type==""]<-9
x$prevtb_type[grepl("^na",x$prevtb_type,ignore.case=TRUE)] <- 99

```



```{r seizures}
x$seizures[grepl("^no",x$seizures,ignore.case=TRUE)] <- 0
x$seizures[grepl("^yes",x$seizures,ignore.case=TRUE)] <- 1
x$seizures[x$seizures==""]<-9
x$seizures[grepl("^na",x$seizures,ignore.case=TRUE)] <- 99
```

```{r hepb}
x$hepb[grepl("^no",x$hepb,ignore.case=TRUE)] <- 0
x$hepb[grepl("^yes",x$hepb,ignore.case=TRUE)] <- 1
x$hepb[x$hepb==""]<-9
x$hepb[grepl("^na",x$hepb,ignore.case=TRUE)] <- 99
```

```{r preg_breastfeed}
x$preg_breastfeed[grepl("^no",x$preg_breastfeed,ignore.case=TRUE)] <- 0
x$preg_breastfeed[grepl("^yes",x$preg_breastfeed,ignore.case=TRUE)] <- 1
x$preg_breastfeed[grepl("^preg",x$preg_breastfeed,ignore.case=TRUE)] <- 1
x$preg_breastfeed[grepl("^brea",x$preg_breastfeed,ignore.case=TRUE)] <- 2
x$preg_breastfeed[x$preg_breastfeed==""]<-9
x$preg_breastfeed[grepl("^na",x$preg_breastfeed,ignore.case=TRUE)] <- 99
```

```{r other comorbid}
x$other_cormorbid[grepl("^no", x$other_cormorbid, ignore.case = TRUE)]<-0
x$other_cormorbid[x$other_cormorbid=="DM"]<-1
x$other_cormorbid[grepl("^dia",x$other_cormorbid,ignore.case=TRUE)] <- 1
x$other_cormorbid[grepl("^hyp",x$other_cormorbid,ignore.case=TRUE)] <- 2
x$other_cormorbid[x$other_cormorbid=="HTN"]<-2
x$other_cormorbid[x$other_cormorbid=="DM_HTN"]<-3
x$other_cormorbid[grepl("^as", x$other_cormorbid, ignore.case = TRUE)]<-4
x$other_cormorbid[grepl("^oth", x$other_cormorbid, ignore.case = TRUE)]<-5
x$other_cormorbid[grepl("^na", x$other_cormorbid, ignore.case = TRUE)]<-99
x$other_cormorbid[grepl("^hep", x$other_cormorbid, ignore.case = TRUE)]<-99
x$other_cormorbid[x$other_cormorbid=="UNKNOWN"]<-9
x$other_cormorbid[x$other_cormorbid==""]<-9
x$other_cormorbid[x$other_cormorbid=="NA"]<-99
x$other_cormorbid[!grepl("[0-99]", x$other_cormorbid, ignore.case = TRUE)]<-99
```

```{r split comorbidities for analysis}
# Creates variables DM for diabetes hits and HTN for hypertension hits
# x$DM<-0
# x$DM[grep(1, x$other_cormorbid)]<-1
# x$DM[grep(3, x$other_cormorbid)]<-1
# x$HTN<-0
# x$HTN[grep(2, x$other_cormorbid)]<-1
# x$HTN[grep(3, x$other_cormorbid)]<-1
```

```{r longterm med}
x$longterm_med[grepl("^no",x$longterm_med,ignore.case=TRUE)] <-0
x$longterm_med[grepl("^dia",x$longterm_med,ignore.case=TRUE)] <-3
x$longterm_med[grepl("^hyper",x$longterm_med,ignore.case=TRUE)] <-4
x$longterm_med[grepl("^tenovir",x$longterm_med,ignore.case=TRUE)] <-1
x$longterm_med[grepl("dmhtn",x$longterm_med,ignore.case=TRUE)] <- 5
x$longterm_med[grepl("hepbdm",x$longterm_med,ignore.case=TRUE)] <- 6
x$longterm_med[grepl("hephtn",x$longterm_med,ignore.case=TRUE)] <- 7
x$longterm_med[grepl("hepbsei",x$longterm_med,ignore.case=TRUE)] <- 8
x$longterm_med[grepl("seizuredm",x$longterm_med,ignore.case=TRUE)] <- 9
x$longterm_med[grepl("seizurehtn",x$longterm_med,ignore.case=TRUE)] <- 10
x$longterm_med[grepl("hep",x$longterm_med,ignore.case=TRUE)] <- 1
x$longterm_med[grepl("seiz",x$longterm_med,ignore.case=TRUE)] <- 2
x$longterm_med[grepl("dm",x$longterm_med,ignore.case=TRUE)] <- 3
x$longterm_med[grepl("other",x$longterm_med,ignore.case=TRUE)] <- 11
x$longterm_med[x$longterm_med==""]<-999
x$longterm_med[grepl("^na",x$longterm_med,ignore.case=TRUE)] <- 99
x$longterm_med[!grepl("[0-99]", x$longterm_med, ignore.case = TRUE)]<-99
```

```{r eversmoked}
x$ever_smoked[grepl("^no",x$ever_smoked,ignore.case=TRUE)] <- 0
x$ever_smoked[grepl("^yes",x$ever_smoked,ignore.case=TRUE)] <- 1
x$ever_smoked[x$ever_smoked==""]<-9
x$ever_smoked[grepl("^na",x$ever_smoked,ignore.case=TRUE)] <- 99
```

```{r bcg tibetborn}
x$bcg_tibetborn[grepl("^no",x$bcg_tibetborn, ignore.case=TRUE)] <- 0
x$bcg_tibetborn[grepl("^yes",x$bcg_tibetborn,ignore.case=TRUE)] <- 1
x$bcg_tibetborn[x$bcg_tibetborn==""]<-9
x$bcg_tibetborn[grepl("^na",x$bcg_tibetborn,ignore.case=TRUE)] <- 99
```

```{r contact with TB in last two years}
x$contactsch_2yr[grepl("^no",x$contactsch_2yr, ignore.case=TRUE)] <- 0
x$contactsch_2yr[grepl("^yes",x$contactsch_2yr,ignore.case=TRUE)] <- 1
x$contactsch_2yr[x$contactsch_2yr==""]<-9
x$contactsch_2yr[grepl("^na",x$contactsch_2yr,ignore.case=TRUE)] <- 99
```

```{r drug sensitivity of Tb case at school}
x$indexcasesch_tbtype[grepl("^non",x$indexcasesch_tbtype, ignore.case=TRUE)] <- 0
x$indexcasesch_tbtype[grepl("^mdr",x$indexcasesch_tbtype,ignore.case=TRUE)] <- 1
x$indexcasesch_tbtype[grepl("^unk",x$indexcasesch_tbtype,ignore.case=TRUE)] <- 9
x$indexcasesch_tbtype[x$indexcasesch_tbtype==""]<-9
x$indexcasesch_tbtype[grepl("^na",x$indexcasesch_tbtype,ignore.case=TRUE)] <- 99
```

```{r index case at school}
x$indexcasesch_is[x$indexcasesch_is=="CLASS MATE"]<-1
x$indexcasesch_is[x$indexcasesch_is=="CLASS-MATE"]<-1
x$indexcasesch_is[x$indexcasesch_is=="CLASSMATE"]<-1
x$indexcasesch_is[x$indexcasesch_is=="DORM MATE"]<-2
x$indexcasesch_is[x$indexcasesch_is=="DORMMATE"]<-2
x$indexcasesch_is[x$indexcasesch_is=="DORM-MATE"]<-2
x$indexcasesch_is[x$indexcasesch_is=="CLASSDORM MATE"]<-3
x$indexcasesch_is[x$indexcasesch_is=="CLASS DORM MATE"]<-3
x$indexcasesch_is[x$indexcasesch_is=="CLASS DORM-MATE"]<-3
x$indexcasesch_is[x$indexcasesch_is=="SCHOOL STAFF"]<-4
x$indexcasesch_is[x$indexcasesch_is=="SCHOOL-STAFF"]<-4
x$indexcasesch_is[x$indexcasesch_is=="FRIEND"]<-5
x$indexcasesch_is[x$indexcasesch_is=="OTHER"]<-6
x$indexcasesch_is[x$indexcasesch_is=="NA"]<-99
x$indexcasesch_count[x$indexcasesch_count=="0"]<-0
x$indexcasesch_count[x$indexcasesch_count=="1"]<-1
x$indexcasesch_count[x$indexcasesch_count=="2"]<-2
x$indexcasesch_count[x$indexcasesch_count=="3"]<-3
x$indexcasesch_count[x$indexcasesch_count=="4"]<-3
x$indexcasesch_count[grepl("^>",x$indexcasesch_count, ignore.case=FALSE)]<-3
x$indexcasesch_count[x$indexcasesch_count=="NA"]<-99
x$indexcasesch_count[x$indexcasesch_count==""]<-9
```

```{r exposed to TB athome}
x$contacthome_2yr[grepl("^no",x$contacthome_2yr, ignore.case=TRUE)] <- 0
x$contacthome_2yr[grepl("^yes",x$contacthome_2yr,ignore.case=TRUE)] <- 1
x$contacthome_2yr[x$contacthome_2yr==""]<-9
x$contacthome_2yr[grepl("^na",x$contacthome_2yr,ignore.case=TRUE)] <- 99
```

```{r drug sensitivity of the TB case at home}
x$indexcasehome_tbtype[grepl("^non",x$indexcasehome_tbtype, ignore.case=TRUE)] <- 0
x$indexcasehome_tbtype[grepl("^mdr",x$indexcasehome_tbtype,ignore.case=TRUE)] <- 1
x$indexcasehome_tbtype[grepl("^unk",x$indexcasehome_tbtype,ignore.case=TRUE)] <- 9
x$indexcasehome_tbtype[x$indexcasehome_tbtype==""]<-9
x$indexcasehome_tbtype[grepl("^na",x$indexcasehome_tbtype,ignore.case=TRUE)] <- 99
```

```{r index case at home}
x$indexcasehome_is[x$indexcasehome_is=="PARENT"]<-1
x$indexcasehome_is[x$indexcasehome_is=="SIBLING"]<-2
x$indexcasehome_is[x$indexcasehome_is=="GRANDPARENT"]<-3
x$indexcasehome_is[x$indexcasehome_is=="GRAND PARENT"]<-3
x$indexcasehome_is[x$indexcasehome_is=="OTHER"]<-4
x$indexcasehome_is[x$indexcasehome_is==""]<-9
x$indexcasehome_is[x$indexcasehome_is=="NA"]<-99
```

```{r indexcasehome_count}
x$indexcasehome_count[x$indexcasehome_count=="0"]<-0
x$indexcasehome_count[x$indexcasehome_count=="1"]<-1
x$indexcasehome_count[x$indexcasehome_count==">1"]<-1
x$indexcasehome_count[x$indexcasehome_count=="2"]<-2
x$indexcasehome_count[x$indexcasehome_count=="3"]<-3
x$indexcasehome_count[x$indexcasehome_count=="4"]<-3
x$indexcasehome_count[x$indexcasehome_count==""]<-9
x$indexcasehome_count[x$indexcasehome_count>="NA"]<-99
#### CHECK THIS LAST LINE OF CODE
```

```{r presence of cough}
x$cough[grepl("^no",x$cough, ignore.case=TRUE)] <- 0
x$cough[grepl("^yes",x$cough,ignore.case=TRUE)] <- 1
x$cough[x$cough==""]<-9
x$cough[grepl("^na",x$cough,ignore.case=TRUE)] <- 99
```


```{r cough duration in weeks}
x$coughduration_wks[grepl("^l", x$coughduration_wks, ignore.case=TRUE)]<-1
x$coughduration_wks[grepl("^<1", x$coughduration_wks, ignore.case=TRUE)]<-1
x$coughduration_wks[grepl("^o", x$coughduration_wks, ignore.case=TRUE)]<-2
x$coughduration_wks[grepl("^1-", x$coughduration_wks, ignore.case=TRUE)]<-2
x$coughduration_wks[grepl("^t", x$coughduration_wks, ignore.case=TRUE)]<-3
x$coughduration_wks[grepl("^2-", x$coughduration_wks, ignore.case=TRUE)]<-3
x$coughduration_wks[grepl("^g", x$coughduration_wks, ignore.case=TRUE)]<-4
x$coughduration_wks[grepl("^3-", x$coughduration_wks, ignore.case=TRUE)]<-4
x$coughduration_wks[grepl("4", x$coughduration_wks, ignore.case=TRUE)]<-4
x$coughduration_wks[grepl("^na", x$coughduration_wks, ignore.case=TRUE)]<-99
x$coughduration_wks[x$coughduration_wks=="NA"]<-99
x$coughduration_wks[!grepl("[0-99]", x$coughduration_wks, ignore.case=TRUE)]<- 9
```

```{r patient cough productive}
x$productive_cough[grepl("^no",x$productive_cough, ignore.case=TRUE)] <- 0
x$productive_cough[grepl("^yes",x$productive_cough,ignore.case=TRUE)] <- 1
x$productive_cough[x$productive_cough==""]<-9
x$productive_cough[grepl("^na",x$productive_cough,ignore.case=TRUE)] <- 99
```

```{r presence of blood in sputum}
x$blood_sputum[grepl("^no",x$blood_sputum, ignore.case=TRUE)] <- 0
x$blood_sputum[grepl("^yes",x$blood_sputum,ignore.case=TRUE)] <- 1
x$blood_sputum[x$blood_sputum==""]<-9
x$blood_sputum[grepl("^na",x$blood_sputum,ignore.case=TRUE)] <- 99
```

```{r fever}
x$fever[grepl("^no",x$fever, ignore.case=TRUE)] <- 0
x$fever[grepl("^yes",x$fever,ignore.case=TRUE)] <- 1
x$fever[x$fever==""]<-9
x$fever[grepl("^na",x$fever,ignore.case=TRUE)] <- 99
```

```{r fever duration}
x$fever_duration[grepl("^l", x$fever_duration, ignore.case = TRUE)]<-1
x$fever_duration[grepl("^<1", x$fever_duration, ignore.case = TRUE)]<-1
x$fever_duration[grepl("^o", x$fever_duration, ignore.case = TRUE)]<-2
x$fever_duration[grepl("^1-", x$fever_duration, ignore.case = TRUE)]<-2
x$fever_duration[grepl("^g", x$fever_duration, ignore.case = TRUE)]<-3
x$fever_duration[grepl("^2-", x$fever_duration, ignore.case = TRUE)]<-3
x$fever_duration[grepl("^>2-", x$fever_duration, ignore.case = TRUE)]<-3
x$fever_duration[grepl("^na", x$fever_duration, ignore.case = TRUE)]<-99
x$fever_duration[x$fever_duration==""]<-9
```

```{r presence of night sweats}
x$nightsweats_2wks[grepl("^no",x$nightsweats_2wks, ignore.case=TRUE)] <- 0
x$nightsweats_2wks[grepl("^yes",x$nightsweats_2wks,ignore.case=TRUE)] <- 1
x$nightsweats_2wks[x$nightsweats_2wks==""]<-9
x$nightsweats_2wks[grepl("^na",x$nightsweats_2wks,ignore.case=TRUE)] <- 99
```

```{r weight loss in year prior}
x$wtloss_1month[grepl("^no",x$wtloss_1month, ignore.case=TRUE)] <- 0
x$wtloss_1month[grepl("no",x$wtloss_1month, ignore.case=TRUE)] <- 0
x$wtloss_1month[grepl("^yes",x$wtloss_1month,ignore.case=TRUE)] <- 1
x$wtloss_1month[grepl("yes",x$wtloss_1month,ignore.case=TRUE)] <- 1
x$wtloss_1month[x$wtloss_1month==""]<-9
x$wtloss_1month[grepl("^na",x$wtloss_1month,ignore.case=TRUE)] <- 99
```

```{r fatigue prior 2 weeks}
x$fatigue_last2wks[grepl("^no",x$fatigue_last2wks, ignore.case=TRUE)] <- 0
x$fatigue_last2wks[grepl("^yes",x$fatigue_last2wks,ignore.case=TRUE)] <- 1
x$fatigue_last2wks[x$fatigue_last2wks==""]<-9
x$fatigue_last2wks[grepl("^na",x$fatigue_last2wks,ignore.case=TRUE)] <- 99
```

```{r ongoing chest pain}
x$chestpain_current[grepl("^no",x$chestpain_current, ignore.case=TRUE)] <- 0
x$chestpain_current[grepl("^yes",x$chestpain_current,ignore.case=TRUE)] <- 1
x$chestpain_current[x$chestpain_current==""]<-9
x$chestpain_current[grepl("^na",x$chestpain_current,ignore.case=TRUE)] <- 99
```



```{r previous tst done}
x$tst1_done[grepl("^yes",x$tst1_done,ignore.case=TRUE)] <- 1
x$tst1_done[grepl("^done",x$tst1_done,ignore.case=TRUE)] <- 1
x$tst1_done[grepl("^no",x$tst1_done,ignore.case=TRUE)] <- 5
x$tst1_done[x$tst1_done=="PREV TB"]<-2
x$tst1_done[x$tst1_done=="PREVTB"]<-2
x$tst1_done[grepl("^prev", x$tst1_done, ignore.case=TRUE)]<-2
x$tst1_done[grepl("indicate", x$tst1_done, ignore.case=TRUE)]<-3
x$tst1_done[grepl("refus", x$tst1_done, ignore.case=TRUE)]<-4
x$tst1_done[grepl("^na", x$tst1_done, ignore.case=TRUE)]<-99
x$tst1_done[x$tst1_done==""]<-9
```

```{r main}
x$tst1_result[grepl("^neg", x$tst1_result, ignore.case=TRUE)]<-0
x$tst1_result[grepl("^pos", x$tst1_result, ignore.case=TRUE)]<-1
x$tst1_result[grepl("^not", x$tst1_result, ignore.case=TRUE)]<-2
x$tst1_result[grepl("^unk", x$tst1_result, ignore.case=TRUE)]<-9
x$tst1_result[x$tst1_result==""]<-9
x$tst1_result[grepl("^na", x$tst1_result, ignore.case=TRUE)]<-99

x$tst1_date_read[x$tst1_date_read=="NA"]<-""

x$tst1_adr[grepl("^no", x$tst1_adr, ignore.case=TRUE)]<-0
x$tst1_adr[grepl("^yes", x$tst1_adr, ignore.case=TRUE)]<-1
x$tst1_adr[grepl("^de", x$tst1_adr, ignore.case=TRUE)]<-1

```


```{r wheal size}
x$wheal1_size[x$wheal1_size=="NA"]<-""
```

```{r date}
x$xpert1_date[x$xpert1_date=="NA"]<-""
```

```{r type of specimen xpert}
x$xpert1_specimen[grepl("^sput", x$xpert1_specimen, ignore.case=TRUE)]<-1
x$xpert1_specimen[grepl("^ga", x$xpert1_specimen, ignore.case=TRUE)]<-2
x$xpert1_specimen[grepl("^pus", x$xpert1_specimen, ignore.case=TRUE)]<-3
x$xpert1_specimen[grepl("^pleu", x$xpert1_specimen, ignore.case=TRUE)]<-4
x$xpert1_specimen[grepl("^uri", x$xpert1_specimen, ignore.case=TRUE)]<-5
x$xpert1_specimen[grepl("^csf", x$xpert1_specimen, ignore.case=TRUE)]<-6
x$xpert1_specimen[grepl("^na", x$xpert1_specimen, ignore.case=TRUE)]<-99
```

```{r result of xpert analysis}
x$xpert1_result[grepl("^pos", x$xpert1_result, ignore.case=TRUE)]<-1
x$xpert1_result[grepl("^ det", x$xpert1_result, ignore.case=TRUE)]<-1
x$xpert1_result[grepl("^det", x$xpert1_result, ignore.case=TRUE)]<-1
x$xpert1_result[grepl("^neg", x$xpert1_result, ignore.case=TRUE)]<-0
x$xpert1_result[grepl("^no", x$xpert1_result, ignore.case=TRUE)]<-0
x$xpert1_result[grepl("^na", x$xpert1_result, ignore.case=TRUE)]<-99

```

```{r drug sensitivty as per xpert analysis}
x$xpert1_mtb[grepl("^vl", x$xpert1_result, ignore.case=TRUE)]<-0
x$xpert1_mtb[grepl("^low", x$xpert1_result, ignore.case=TRUE)]<-1
x$xpert1_mtb[grepl("^med", x$xpert1_result, ignore.case=TRUE)]<-2
x$xpert1_mtb[grepl("^hi", x$xpert1_result, ignore.case=TRUE)]<-3
x$xpert1_mtb[grepl("^na", x$xpert1_result, ignore.case=TRUE)]<-99

```

```{r rifampin resistance}

x$xpert1_rif[grepl("^sen", x$xpert1_rif, ignore.case=TRUE)]<-0
x$xpert1_rif[grepl("^res", x$xpert1_rif, ignore.case=TRUE)]<-1
x$xpert1_rif[grepl("^indet", x$xpert1_rif, ignore.case=TRUE)]<-2
x$xpert1_rif[grepl("^na", x$xpert1_rif, ignore.case=TRUE)]<-99
```

```{r xpert2 date}
x$xpert2_date[x$xpert2_date=="NA"]<-""
```

```{r type of spec use for 2nd xpert}
x$xpert2_specimen[grepl("^sput", x$xpert2_specimen, ignore.case=TRUE)]<-1
x$xpert2_specimen[grepl("^ga", x$xpert2_specimen, ignore.case=TRUE)]<-2
x$xpert2_specimen[grepl("^pus", x$xpert2_specimen, ignore.case=TRUE)]<-3
x$xpert2_specimen[grepl("^pleu", x$xpert2_specimen, ignore.case=TRUE)]<-4
x$xpert2_specimen[grepl("^uri", x$xpert2_specimen, ignore.case=TRUE)]<-5
x$xpert2_specimen[grepl("^csf", x$xpert2_specimen, ignore.case=TRUE)]<-6
x$xpert2_specimen[grepl("^yes", x$xpert2_specimen, ignore.case=TRUE)]<-7
x$xpert2_specimen[grepl("^na", x$xpert2_specimen, ignore.case=TRUE)]<-99
```

```{r result of xpert2}
x$xpert2_result[grepl("^pos", x$xpert2_result, ignore.case=TRUE)]<-1
x$xpert2_result[grepl("^ det", x$xpert2_result, ignore.case=TRUE)]<-1
x$xpert2_result[grepl("^det", x$xpert2_result, ignore.case=TRUE)]<-1
x$xpert2_result[grepl("^neg", x$xpert2_result, ignore.case=TRUE)]<-0
x$xpert2_result[grepl("^no", x$xpert2_result, ignore.case=TRUE)]<-0
x$xpert2_result[grepl("^ab", x$xpert2_result, ignore.case=TRUE)]<-2
x$xpert2_result[grepl("^norm", x$xpert2_result, ignore.case=TRUE)]<-3
x$xpert2_result[grepl("^na", x$xpert2_result, ignore.case=TRUE)]<-99

```


```{r drug sensitivty as per xpert2 analysis}

x$xpert2_mtb[grepl("^vl", x$xpert2_result, ignore.case=TRUE)]<-0
x$xpert2_mtb[grepl("^low", x$xpert2_result, ignore.case=TRUE)]<-1
x$xpert2_mtb[grepl("^med", x$xpert2_result, ignore.case=TRUE)]<-2
x$xpert2_mtb[grepl("^hi", x$xpert2_result, ignore.case=TRUE)]<-3
x$xpert2_mtb[grepl("^na", x$xpert2_result, ignore.case=TRUE)]<-99

```

```{r rifampin resistance 2}

x$xpert2_rif[grepl("^sen", x$xpert2_rif, ignore.case=TRUE)]<-0
x$xpert2_rif[grepl("^res", x$xpert2_rif, ignore.case=TRUE)]<-1
x$xpert2_rif[grepl("^indet", x$xpert2_rif, ignore.case=TRUE)]<-2
x$xpert2_rif[grepl("^na", x$xpert2_rif, ignore.case=TRUE)]<-99

```

```{r cxr}
x$cxr[x$cxr=="NA"]<-""
```

```{r diagnosed with active TB}
x$tb_diagnosed[grepl("^no", x$tb_diagnosed, ignore.case=TRUE)]<-0
x$tb_diagnosed[grepl("^y", x$tb_diagnosed, ignore.case=TRUE)]<-1
x$tb_diagnosed[grepl("^na", x$tb_diagnosed, ignore.case=TRUE)]<-99
```

```{r total num of students}
x$total_students[x$total_students=="NA"]<-""
x$total_staff[x$total_staff=="NA"]<-""
```

```{r total staff}
x$total_monks_nuns[x$total_monks_nuns=="NA"]<-""
```

```{r notes main}
x$notes_main[x$notes_main=="NA"]<-""
x$notes[x$notes=="NA"]<-""
```

```{r demographics}
x$main_database_demographics_complete<-2
```


##ACTIVE TB INVESTIGATION

```{r Active Tb Tbinvestigation}
x$prevtb_dst[x$prevtb_dst=="YES"]<-1
x$prevtb_dst[x$prevtb_dst=="NO"]<-0
x$prevtb_dst[x$prevtb_dst=="NA"]<-99
x$prevtb_dst[x$prevtb_dst=="UNKNOWN"]<-9

x$comorbidity[x$comorbidity=="None"]<-0
x$comorbidity[x$comorbidity=="NONE"]<-0
x$comorbidity[x$comorbidity=="NO"]<-0
x$comorbidity[x$comorbidity=="DM"]<-1
x$comorbidity[x$comorbidity=="HTN"]<-2
x$comorbidity[x$comorbidity=="DM_HTN"]<-3
x$comorbidity[x$comorbidity=="Other"]<-4
x$comorbidity[x$comorbidity=="OTHER"]<-4
x$comorbidity[x$comorbidity=="NA"]<-99

x$chronic_meds[x$chronic_meds=="NO"]<-0
x$chronic_meds[x$chronic_meds=="YES"]<-
  
x$contact_sch_oneyr[x$contact_sch_oneyr=="NO"]<-0
x$contact_sch_oneyr[x$contact_sch_oneyr=="YES"]<-1
x$contact_sch_oneyr[x$contact_sch_oneyr=="UNKNOWN"]<-9
x$contact_sch_oneyr[x$contact_sch_oneyr=="NA"]<-99

x$indexcasesch_lung_pleura[x$indexcasesch_lung_pleura=="NO"]<-0
x$indexcasesch_lung_pleura[grepl("^n", x$indexcasesch_lung_pleura, ignore.case = TRUE)]<-0
x$indexcasesch_lung_pleura[grepl("^l", x$indexcasesch_lung_pleura, ignore.case = TRUE)]<-1
x$indexcasesch_lung_pleura[x$indexcasesch_lung_pleura=="NA"]<-99

x$indexcasesch_sputumstatus[grepl("^N",x$indexcasesch_sputumstatus,ignore.case=FALSE)] <- 0
x$indexcasesch_sputumstatus[grepl("^n",x$indexcasesch_sputumstatus,ignore.case=FALSE)] <- 0
x$indexcasesch_sputumstatus[grepl("^P",x$indexcasesch_sputumstatus,ignore.case=FALSE)] <- 1
x$indexcasesch_sputumstatus[grepl("^p",x$indexcasesch_sputumstatus,ignore.case=FALSE)] <- 1

x$indexcasesch_sputumstatus[x$indexcasesch_sputumstatus=="UNKNOWN"]<-9
x$indexcasesch_sputumstatus[x$indexcasesch_sputumstatus=="NA"]<-99

x$indexcasesch_dst[grepl("^no",x$indexcasesch_dst,ignore.case=FALSE)] <- 0
x$indexcasesch_dst[grepl("^y",x$indexcasesch_dst,ignore.case=FALSE)] <- 1
x$indexcasesch_dst[grepl("^u",x$indexcasesch_dst,ignore.case=FALSE)] <- 9
x$indexcasesch_dst[grepl("^na",x$indexcasesch_dst,ignore.case=FALSE)] <- 99

x$indexcasesch_cough[x$indexcasesch_cough=="NO"]<-0
x$indexcasesch_cough[x$indexcasesch_cough=="YES"]<-1

x$sharedroom_with_indexcasesch[x$sharedroom_with_indexcasesch=="NO"]<-0
x$sharedroom_with_indexcasesch[x$sharedroom_with_indexcasesch=="YES"]<-1

x$relation_with_indexcasesch[x$relation_with_indexcasesch=="CLASS-MATE"]<-1
x$relation_with_indexcasesch[x$relation_with_indexcasesch=="CLASS MATE"]<-1
x$relation_with_indexcasesch[x$relation_with_indexcasesch=="DORM-MATE"]<-2
x$relation_with_indexcasesch[x$relation_with_indexcasesch=="DORM MATE"]<-2
x$relation_with_indexcasesch[x$relation_with_indexcasesch=="CLASSDORM-MATE"]<-3
x$relation_with_indexcasesch[x$relation_with_indexcasesch=="CLASSDORM MATE"]<-3
x$relation_with_indexcasesch[x$relation_with_indexcasesch=="SCHOOL-STAFF"]<-4
x$relation_with_indexcasesch[x$relation_with_indexcasesch=="SCHOOL STAFF"]<-4
x$relation_with_indexcasesch[x$relation_with_indexcasesch=="FRIEND"]<-5
x$relation_with_indexcasesch[x$relation_with_indexcasesch=="OTHER"]<-6
x$relation_with_indexcasesch[x$relation_with_indexcasesch=="NA"]<-99

x$indexcasehome_lung[x$indexcasehome_lung=="NO"]<-0
x$indexcasehome_lung[x$indexcasehome_lung=="YES"]<-1
x$indexcasehome_lung[x$indexcasehome_lung=="NA"]<-99

x$indexcasehome_dst[grepl("^no",x$indexcasehome_dst,ignore.case=FALSE)] <- 0
x$indexcasehome_dst[grepl("^y",x$indexcasehome_dst,ignore.case=FALSE)] <- 1
x$indexcasehome_dst[grepl("^u",x$indexcasehome_dst,ignore.case=FALSE)] <- 9
x$indexcasehome_dst[grepl("^na",x$indexcasehome_dst,ignore.case=FALSE)] <- 99

x$indexcasehome_sputumstatus[x$indexcasehome_sputumstatus=="NEGATIVE"]<-0
x$indexcasehome_sputumstatus[x$indexcasehome_sputumstatus=="POSITIVE"]<-1
x$indexcasehome_sputumstatus[x$indexcasehome_sputumstatus=="NOT DONE"]<-2
x$indexcasehome_sputumstatus[x$indexcasehome_sputumstatus=="UNKNOWN"]<-9

x$indexcasehome_cough[x$indexcasehome_cough=="NO"]<-0
x$indexcasehome_cough[x$indexcasehome_cough=="YES"]<-1
x$indexcasehome_cough[x$indexcasehome_cough=="NA"]<-99

x$sharedroom_with_indexcasehome[x$sharedroom_with_indexcasehome=="NO"]<-0
x$sharedroom_with_indexcasehome[x$sharedroom_with_indexcasehome=="YES"]<-1

x$relation_with_indexcasehome[x$relation_with_indexcasehome=="PARENT"]<-1
x$relation_with_indexcasehome[x$relation_with_indexcasehome=="SIBLING"]<-2
x$relation_with_indexcasehome[x$relation_with_indexcasehome=="GRANDPARENT"]<-3
x$relation_with_indexcasehome[x$relation_with_indexcasehome=="GRAND PARENT"]<-3
x$relation_with_indexcasehome[x$relation_with_indexcasehome=="OTHER"]<-4
x$relation_with_indexcasehome[x$relation_with_indexcasehome=="NA"]<-99
x$relation_with_indexcasehome[x$relation_with_indexcasehome=="PARENT"]<-1
x$relation_with_indexcasehome[x$relation_with_indexcasehome=="SIBLING"]<-2
x$relation_with_indexcasehome[x$relation_with_indexcasehome=="GRANDPARENT"]<-3
x$relation_with_indexcasehome[x$relation_with_indexcasehome=="GRAND PARENT"]<-3
x$relation_with_indexcasehome[x$relation_with_indexcasehome=="OTHER"]<-4
x$relation_with_indexcasehome[x$relation_with_indexcasehome=="NA"]<-99

x$cxr_date[x$cxr_date=="NA"]<-""

x$cxr_finding[x$cxr_finding=="NA"]<-""

x$followup_advised[x$followup_advised=="NA"]<-""
x$followup_complete[x$followup_complete=="NA"]<-""

x$tb_diagnosis[x$tb_diagnosis=="NO"]<-0
x$tb_diagnosis[x$tb_diagnosis=="YES"]<-1

x$sch_mon_prev1yr[x$sch_mon_prev1yr=="TCV LADHAK"]<-20
x$sch_mon_prev1yr[x$sch_mon_prev1yr=="BYLAKUPPE"]<-19
x$sch_mon_prev1yr[x$sch_mon_prev1yr=="SELAQUI"]<-12
x$sch_mon_prev1yr[x$sch_mon_prev1yr=="GTCV"]<-3
x$sch_mon_prev1yr[x$sch_mon_prev1yr=="LTCV"]<-1
x$sch_mon_prev1yr[x$sch_mon_prev1yr=="STS POANTA"]<-10

x$doh_index_no[x$doh_index_no=="NA"]<-NA

x$patient_type[x$patient_type=="NEW"]<-1
x$patient_type[grepl("^RE", x$patient_type, ignore.case = TRUE)]<-2

x$disease_site[grepl("NA",x$disease_site,ignore.case=TRUE)] <- ""
x$disease_site[grepl("LUNG",x$disease_site,ignore.case=TRUE)] <-1
x$disease_site[grepl("^PLE",x$disease_site,ignore.case=TRUE)] <-2
x$disease_site[grepl("LUNG & PLEURA",x$disease_site,ignore.case=TRUE)] <-3
x$disease_site[grepl("^LYMPH",x$disease_site,ignore.case=TRUE)] <-4
x$disease_site[grepl("^AB",x$disease_site,ignore.case=TRUE)] <-5
x$disease_site[grepl("^SP",x$disease_site,ignore.case=TRUE)] <-6
x$disease_site[grepl("^BONE",x$disease_site,ignore.case=TRUE)] <-7
x$disease_site[grepl("OTHER BONE",x$disease_site,ignore.case=TRUE)] <-7
x$disease_site[grepl("OTHER",x$disease_site,ignore.case=TRUE)] <-8

x$category[grepl("NA",x$category,ignore.case=TRUE)] <- ""
x$category[grepl("^CAT-1",x$category,ignore.case=TRUE)] <- 1
x$category[grepl("^CAT-2",x$category,ignore.case=TRUE)] <- 2
x$category[grepl("^CAT-4",x$category,ignore.case=TRUE)] <- 3
x$category[grepl("^IN",x$category,ignore.case=TRUE)] <- 4
x$category[grepl("^NT",x$category,ignore.case=TRUE)] <- 5

x$place_rx_start[x$place_rx_start=="NA"]<-""

x$date_rx_start[x$date_rx_start=="NA"]<-""

x$diagnostic_smear[grepl("^NA",x$diagnostic_smear,ignore.case=TRUE)] <- ""
x$diagnostic_smear[grepl("^UNKNO",x$diagnostic_smear,ignore.case=TRUE)] <- 9
x$diagnostic_smear[grepl("^P",x$diagnostic_smear,ignore.case=TRUE)] <- 1
x$diagnostic_smear[grepl("^N",x$diagnostic_smear,ignore.case=TRUE)] <- 0
x$diagnostic_smear[grepl("^NOT",x$diagnostic_smear,ignore.case=TRUE)] <- 2
x$diagnostic_smear[x$diagnostic_smear=="SCANTY"]<-3

x$hiv[grepl("^NA",x$hiv,ignore.case=TRUE)] <- ""
x$hiv[grepl("^N",x$hiv,ignore.case=TRUE)] <- 0
x$hiv[grepl("^P",x$hiv,ignore.case=TRUE)] <- 1
x$hiv[grepl("^NOT",x$hiv,ignore.case=TRUE)] <- 2
x$hiv[grepl("^UNK",x$hiv,ignore.case=TRUE)] <- 9

x$hep_b[grepl("^NA",x$hep_b,ignore.case=TRUE)] <- ""
x$hep_b[grepl("^N",x$hep_b,ignore.case=TRUE)] <- 0
x$hep_b[grepl("^P",x$hep_b,ignore.case=TRUE)] <- 1
x$hep_b[grepl("^NOT",x$hep_b,ignore.case=TRUE)] <- 2
x$hep_b[grepl("^UNK",x$hep_b,ignore.case=TRUE)] <- 9

x$culture_result[grepl("^NA",x$culture_result,ignore.case=TRUE)] <- ""
x$culture_result[grepl("^NO",x$culture_result,ignore.case=TRUE)] <- 3
x$culture_result[grepl("^N",x$culture_result,ignore.case=TRUE)] <- 0
x$culture_result[grepl("^P",x$culture_result,ignore.case=TRUE)] <- 1
x$culture_result[grepl("^NOT",x$culture_result,ignore.case=TRUE)] <- 2
x$culture_result[grepl("^UNK",x$culture_result,ignore.case=TRUE)] <- 9

x$dst_inh[grepl("^NA",x$dst_inh,ignore.case=TRUE)] <- ""
x$dst_inh[grepl("^SEN",x$dst_inh,ignore.case=TRUE)] <- 0
x$dst_inh[grepl("^RES",x$dst_inh,ignore.case=TRUE)] <- 1
x$dst_inh[grepl("^NOT",x$dst_inh,ignore.case=TRUE)] <- 2
x$dst_inh[grepl("^UNK",x$dst_inh,ignore.case=TRUE)] <- 9

x$dst_rif[grepl("^NA",x$dst_rif,ignore.case=TRUE)] <- ""
x$dst_rif[grepl("^SEN",x$dst_rif,ignore.case=TRUE)] <- 0
x$dst_rif[grepl("^RES",x$dst_rif,ignore.case=TRUE)] <- 1
x$dst_rif[grepl("^NOT",x$dst_rif,ignore.case=TRUE)] <- 2
x$dst_rif[grepl("^UNK",x$dst_rif,ignore.case=TRUE)] <- 9

x$dst_etham[grepl("^NA",x$dst_etham,ignore.case=TRUE)] <- ""
x$dst_etham[grepl("^SEN",x$dst_etham,ignore.case=TRUE)] <- 0
x$dst_etham[grepl("^RES",x$dst_etham,ignore.case=TRUE)] <- 1
x$dst_etham[grepl("^NOT",x$dst_etham,ignore.case=TRUE)] <- 2
x$dst_etham[grepl("^UNK",x$dst_etham,ignore.case=TRUE)] <- 9

x$dst_pza[grepl("^NA",x$dst_pza,ignore.case=TRUE)] <- ""
x$dst_pza[grepl("^SEN",x$dst_pza,ignore.case=TRUE)] <- 0
x$dst_pza[grepl("^RES",x$dst_pza,ignore.case=TRUE)] <- 1
x$dst_pza[grepl("^NOT",x$dst_pza,ignore.case=TRUE)] <- 2
x$dst_pza[grepl("^UNK",x$dst_pza,ignore.case=TRUE)] <- 9

x$dst_ofx[grepl("^NA",x$dst_ofx,ignore.case=TRUE)] <- ""
x$dst_ofx[grepl("^SEN",x$dst_ofx,ignore.case=TRUE)] <- 0
x$dst_ofx[grepl("^RES",x$dst_ofx,ignore.case=TRUE)] <- 1
x$dst_ofx[grepl("^NOT",x$dst_ofx,ignore.case=TRUE)] <- 2
x$dst_ofx[grepl("^UNK",x$dst_ofx,ignore.case=TRUE)] <- 9

x$dst_mfx[grepl("^NA",x$dst_mfx,ignore.case=TRUE)] <- ""
x$dst_mfx[grepl("^SEN",x$dst_mfx,ignore.case=TRUE)] <- 0
x$dst_mfx[grepl("^RES",x$dst_mfx,ignore.case=TRUE)] <- 1
x$dst_mfx[grepl("^NOT",x$dst_mfx,ignore.case=TRUE)] <- 2
x$dst_mfx[grepl("^UNK",x$dst_mfx,ignore.case=TRUE)] <- 9

x$dst_km[grepl("^NA",x$dst_km,ignore.case=TRUE)] <- ""
x$dst_km[grepl("^SEN",x$dst_km,ignore.case=TRUE)] <- 0
x$dst_km[grepl("^RES",x$dst_km,ignore.case=TRUE)] <- 1
x$dst_km[grepl("^NOT",x$dst_km,ignore.case=TRUE)] <- 2
x$dst_km[grepl("^UNK",x$dst_km,ignore.case=TRUE)] <- 9

x$dst_sm[grepl("^NA",x$dst_sm,ignore.case=TRUE)] <- ""
x$dst_sm[grepl("^SEN",x$dst_sm,ignore.case=TRUE)] <- 0
x$dst_sm[grepl("^RES",x$dst_sm,ignore.case=TRUE)] <- 1
x$dst_sm[grepl("^NOT",x$dst_sm,ignore.case=TRUE)] <- 2
x$dst_sm[grepl("^UNK",x$dst_sm,ignore.case=TRUE)] <- 9

x$dst_am[grepl("^NA",x$dst_am,ignore.case=TRUE)] <- ""
x$dst_am[grepl("^SEN",x$dst_am,ignore.case=TRUE)] <- 0
x$dst_am[grepl("^RES",x$dst_am,ignore.case=TRUE)] <- 1
x$dst_am[grepl("^NOT",x$dst_am,ignore.case=TRUE)] <- 2
x$dst_am[grepl("^UNK",x$dst_am,ignore.case=TRUE)] <- 9

x$dst_cm[grepl("^NA",x$dst_cm,ignore.case=TRUE)] <- ""
x$dst_cm[grepl("^SEN",x$dst_cm,ignore.case=TRUE)] <- 0
x$dst_cm[grepl("^RES",x$dst_cm,ignore.case=TRUE)] <- 1
x$dst_cm[grepl("^NOT",x$dst_cm,ignore.case=TRUE)] <- 2
x$dst_cm[grepl("^UNK",x$dst_cm,ignore.case=TRUE)] <- 9

x$dst_ethio[grepl("^NA",x$dst_ethio,ignore.case=TRUE)] <- ""
x$dst_ethio[grepl("^SEN",x$dst_ethio,ignore.case=TRUE)] <- 0
x$dst_ethio[grepl("^RES",x$dst_ethio,ignore.case=TRUE)] <- 1
x$dst_ethio[grepl("^NOT",x$dst_ethio,ignore.case=TRUE)] <- 2
x$dst_ethio[grepl("^UNK",x$dst_ethio,ignore.case=TRUE)] <- 9

x$dst_pas[grepl("^NA",x$dst_pas,ignore.case=TRUE)] <- ""
x$dst_pas[grepl("^SEN",x$dst_pas,ignore.case=TRUE)] <- 0
x$dst_pas[grepl("^RES",x$dst_pas,ignore.case=TRUE)] <- 1
x$dst_pas[grepl("^NOT",x$dst_pas,ignore.case=TRUE)] <- 2
x$dst_pas[grepl("^UNK",x$dst_pas,ignore.case=TRUE)] <- 9

x$dst_clf[grepl("^NA",x$dst_clf,ignore.case=TRUE)] <- ""
x$dst_clf[grepl("^SEN",x$dst_clf,ignore.case=TRUE)] <- 0
x$dst_clf[grepl("^RES",x$dst_clf,ignore.case=TRUE)] <- 1
x$dst_clf[grepl("^NOT",x$dst_clf,ignore.case=TRUE)] <- 2
x$dst_clf[grepl("^UNK",x$dst_clf,ignore.case=TRUE)] <- 9

x$smear_conv[x$smear_conv=="HALF-MONTH"]<-1
x$smear_conv[x$smear_conv=="NA"]<-99

x$end_rx_smear[grepl("^NA",x$end_rx_smear,ignore.case=TRUE)] <- ""
x$end_rx_smear[grepl("^U",x$end_rx_smear,ignore.case=TRUE)] <-9
x$end_rx_smear[grepl("^NOT",x$end_rx_smear,ignore.case=TRUE)] <- 2
x$end_rx_smear[grepl("^NEG",x$end_rx_smear,ignore.case=TRUE)] <- 0
x$end_rx_smear[grepl("^POS",x$end_rx_smear,ignore.case=TRUE)] <- 1

x$date_rx_stoppped[x$date_rx_stopped=="NA"]<-""

x$rx_outcome[grepl("^NA",x$rx_outcome,ignore.case=TRUE)] <- ""
x$rx_outcome[grepl("^CU",x$rx_outcome,ignore.case=TRUE)] <- 1
x$rx_outcome[grepl("^CO",x$rx_outcome,ignore.case=TRUE)] <- 2
x$rx_outcome[grepl("^F",x$rx_outcome,ignore.case=TRUE)] <- 3
x$rx_outcome[grepl("^D",x$rx_outcome,ignore.case=TRUE)] <- 4
x$rx_outcome[grepl("^L",x$rx_outcome,ignore.case=TRUE)] <- 5
```

```{r complete}
x$main_database_demographics_complete<-2
x$main_database_tbinvestigation_complete<-2
x$active_tb_tbinvestigation_complete<-2
x$tst_reactive_treatment_complete<-2
```

##TST REACTIVE TREATMENT

```{r reactive TB}
x$prev_therapy[grepl("NA",x$prev_therapy,ignore.case=TRUE)]<-""
x$prev_therapy[grepl("RECE",x$prev_therapy,ignore.case=TRUE)]<-1
x$prev_therapy[grepl("^NOT RECE",x$prev_therapy,ignore.case=TRUE)]<-2
x$prev_therapy[grepl("^C",x$prev_therapy,ignore.case=TRUE)]<-3
x$prev_therapy[grepl("^NOT RE",x$prev_therapy,ignore.case=TRUE)]<-5
x$prev_therapy[grepl("^A",x$prev_therapy,ignore.case=TRUE)]<-6
x$prev_therapy[grepl("^TB",x$prev_therapy,ignore.case=TRUE)]<-6

x$prev_ther_no[x$prev_ther_no=="NA"]<-""

x$prev_therapy_reg[grepl("NA",x$prev_therapy_reg,ignore.case=TRUE)]<-""
x$prev_therapy_reg[grepl("4R",x$prev_therapy_reg,ignore.case=TRUE)]<-1
x$prev_therapy_reg[grepl("3HR",x$prev_therapy_reg,ignore.case=TRUE)]<-2
x$prev_therapy_reg[grepl("6H",x$prev_therapy_reg,ignore.case=TRUE)]<-3
x$prev_therapy_reg[grepl("3HP",x$prev_therapy_reg,ignore.case=TRUE)]<-4
x$prev_therapy_reg[grepl("NA",x$prev_therapy_reg,ignore.case=TRUE)]<-99

x$prevther_startdate[x$prevther_startdate=="NA"]<-""

x$prevther_adr[grepl("NA",x$prevther_adr,ignore.case=TRUE)]<-99
x$prevther_adr[grepl("^N",x$prevther_adr,ignore.case=TRUE)]<-0
x$prevther_adr[grepl("^Y",x$prevther_adr,ignore.case=TRUE)]<-1

x$typeofadr[x$typeofadr=="NA"]<-""

x$culprit_drug[grepl("NA",x$culprit_drug ,ignore.case=TRUE)]<-99
x$culprit_drug[grepl("Rif",x$culprit_drug,ignore.case=TRUE)]<-1
x$culprit_drug[grepl("^I",x$culprit_drug,ignore.case=TRUE)]<-2
x$culprit_drug[grepl("Rif-Inh",x$culprit_drug,ignore.case=TRUE)]<-3

x$ptsa_gi[x$ptsa_gi=="NO"]<-0
x$ptsa_gi[x$ptsa_gi=="YES"]<-1
x$ptsa_gi[x$ptsa_gi=="NA"]<-99

x$ptsa_red[x$ptsa_red=="NO"]<-0
x$ptsa_red[x$ptsa_red=="YES"]<-1
x$ptsa_red[x$ptsa_red=="NA"]<-99

x$ptsa_sleep[x$ptsa_sleep=="NO"]<-0
x$ptsa_sleep[x$ptsa_sleep=="YES"]<-1
x$ptsa_sleep[x$ptsa_sleep=="NA"]<-99

x$ptsa_head[x$ptsa_head=="NO"]<-0
x$ptsa_head[x$ptsa_head=="YES"]<-1
x$ptsa_head[x$ptsa_head=="NA"]<-99

x$ptsa_jaundice[x$ptsa_jaundice=="NO"]<-0
x$ptsa_jaundice[x$ptsa_jaundice=="YES"]<-1
x$ptsa_jaundice[x$ptsa_jaundice=="NA"]<-99

x$ptsa_rash[x$ptsa_rash=="NO"]<-0
x$ptsa_rash[x$ptsa_rash=="YES"]<-1
x$ptsa_rash[x$ptsa_rash=="NA"]<-99

x$ptsa_hepa[x$ptsa_hepa=="NO"]<-0
x$ptsa_hepa[x$ptsa_hepa=="YES"]<-1
x$ptsa_hepa[x$ptsa_hepa=="NA"]<-99

x$totalbil_1[grepl("NA",x$totalbil_1 ,ignore.case=TRUE)]<-""

x$directl_1[grepl("NA",x$directl_1,ignore.case=TRUE)]<-""

x$sgpt_1[grepl("NA",x$sgpt_1,ignore.case=TRUE)]<-""
x$sgot_1[grepl("NA",x$sgot_1,ignore.case=TRUE)]<-""

x$totalbil_2[grepl("NA",x$totalbil_2,ignore.case=TRUE)]<-""

x$directbil_2[grepl("NA", x$directbil_2,ignore.case=TRUE)]<-""

x$sgpt_2[grepl("NA",x$sgpt_2,ignore.case=TRUE)]<-""
x$sgot_2[grepl( "NA",x$sgot_2,ignore.case=TRUE)]<-""

x$totalbil_3[grepl("NA",x$totalbil_3,ignore.case=TRUE)]<-""

x$directbil_3[grepl("NA",x$directbil_3,ignore.case=TRUE)]<-""

x$sgpt_3[grepl("NA",x$sgpt_3,ignore.case=TRUE)]<-""
x$sgot_3[grepl("NA",x$sgot_3,ignore.case=TRUE)]<-""

x$totalbil_4[grepl("NA",x$totalbil_4,ignore.case=TRUE)]<-""

x$directbil_4[grepl("NA",x$directbil_4,ignore.case=TRUE)]<-""

x$sgpt_4[grepl("NA",x$sgpt_4,ignore.case=TRUE)]<-""
x$sgot_4[grepl("NA",x$sgot_4,ignore.case=TRUE)]<-"" 

x$prevtherapy_held[grepl("NA",x$prevtherapy_held,ignore.case=TRUE)]<-99
x$prevtherapy_held[grepl("^N",x$prevtherapy_held,ignore.case=TRUE)]<-0
x$prevtherapy_held[grepl("^Y",x$prevtherapy_held,ignore.case=TRUE)]<-1

x$date_prevther_held[x$date_prevther_held=="NA"]<-""
x$date_prevther_restarted[x$date_prevther_restarted=="NA"]<-""

x$prev_therapy_revised[grepl("NA",x$prev_therapy_revised,ignore.case=TRUE)]<-99
x$prev_therapy_revised[grepl("^N",x$prev_therapy_revised,ignore.case=TRUE)]<-0
x$prev_therapy_revised[grepl("^Y",x$prev_therapy_revised,ignore.case=TRUE)]<-1

x$revised_prevther_reg[grepl("NA",x$revised_prevther_reg,ignore.case=TRUE)]<-""
x$revised_prevther_reg[grepl("^4",x$revised_prevther_reg,ignore.case=TRUE)]<-1
x$revised_prevther_reg[grepl("^3HR",x$revised_prevther_reg,ignore.case=TRUE)]<-2
x$revised_prevther_reg[grepl("^6",x$revised_prevther_reg,ignore.case=TRUE)]<-3
x$revised_prevther_reg[grepl("^3HP",x$revised_prevther_reg,ignore.case=TRUE)]<-4
x$revised_prevther_reg[!grepl("^4|^3HR|^6|^3HP|^NA", x$revised_prevther_reg,ignore.case=TRUE)]<- ""

x$prevther_outcome[grepl("NA",x$prevther_outcome,ignore.case=TRUE)]<-""
x$prevther_outcome[grepl("^COM",x$prevther_outcome,ignore.case=TRUE)]<-1
x$prevther_outcome[grepl("^L",x$prevther_outcome,ignore.case=TRUE)]<-2
x$prevther_outcome[grepl("^A",x$prevther_outcome,ignore.case=TRUE)]<-3
x$prevther_outcome[grepl("TB",x$prevther_outcome,ignore.case=TRUE)]<-3
x$prevther_outcome[!grepl("NA|^COM|^L|^A|TB", x$prevther_outcome,ignore.case=TRUE)]<- 4

x$if_other_specify[x$if_other_specify=="NA"]<-""

x$prevther_stopped_premature[grepl("NA",x$prevther_stopped_premature,ignore.case=TRUE)]<-99
x$prevther_stopped_premature[grepl("^N",x$prevther_stopped_premature,ignore.case=TRUE)]<-0
x$prevther_stopped_premature[grepl("^Y",x$prevther_stopped_premature,ignore.case=TRUE)]<-1

x$prevther_stopped_reason[grepl("NA",x$prevther_stopped_reason,ignore.case=TRUE)]<-99
x$prevther_stopped_reason[grepl("^H",x$prevther_stopped_reason,ignore.case=TRUE)]<- 1
x$prevther_stopped_reason[grepl("^other tox",x$prevther_stopped_reason,ignore.case=TRUE)]<- 2
x$prevther_stopped_reason[grepl("^discont",x$prevther_stopped_reason,ignore.case=TRUE)]<- 3
x$prevther_stopped_reason[!grepl("^H|^other tox|^discont", x$prevther_stopped_reason,ignore.case=TRUE)]<- 4

x$tst_reactive_treatment_complete[x$tst_reactive_treatment_complete=="INCOMPLETE"]<-0
x$tst_reactive_treatment_complete[x$tst_reactive_treatment_complete=="UNVERIFIED"]<-1
x$tst_reactive_treatment_complete[x$tst_reactive_treatment_complete=="COMPLETE"]<-2

x$prevther_startdate[grepl("NA",x$prevther_startdate,ignore.case=TRUE)]<-""

x$date_prevther_held[grepl("NA",x$date_prevther_held,ignore.case=TRUE)]<-""
x$date_prevther_restarted[grepl("NA",x$date_prevther_restarted,ignore.case=TRUE)]<-""

x$date_rx_start = mdy(x$date_rx_start)
x$date_rx_stopped = mdy(x$date_rx_stopped)

x$main_database_demographics_complete<-2
x$main_database_tbinvestigation_complete<-2
x$active_tb_tbinvestigation_complete<-2
x$tst_reactive_treatment_complete<-2
```


```{r export}
write.csv(x,"~/Zero TB in Kids/ztbtk_data_clean/Lower_TCV_Main_CLEAN.csv", na="")
```