---
title: "maindatabase"
author: "Gopika Punchhi"
date: "12/11/2019"
output: html_document
---

This document only contain code for demographic variables as listed in the redcap dictionary. It is unlikely that you will use this document alone without any additional variables. 

Before running this document, change x=read.csv("LOCATION OF FILE TO READ IN", ......)
At the bottom of the document, change write.csv to the appropriate document name and location to save the new csv file for upload to REDCap

in the excel sheet, you need to assign the case designation variable to active tb once you have converted to the new csv file using the code below
```{r institute, include=FALSE}
library(plyr)
library(readr)
library(dplyr)
library(tidyverse)
library(lubridate)
x=read.csv("C:/Users/g_pun/Dropbox/ZeroTB/STCV/CT_TST_REAC.csv",stringsAsFactors = FALSE, na.strings=TRUE)
##Insitute variable renaming
##need to write this in based on what you see in the document
x$institute[x$institute=="LTCV"]<-1
x$institute[x$institute=="LowerTCV"]<-1
x$institute[x$institute=="GTCV"]<-3
x$institute[x$institute=="TCV GOPUR"]<-3
x$institute[x$institute=="LTCV"]<-1
x$institute[x$institute=="LTCV"]<-1
x$institute[x$institute=="STSP"]<-10
x$institute[x$institute=="STCV"]<-4
```

```{r age}
x$age[x$age=="NA"]<-""
```

```{r sex}
x$sex[grepl("^m", x$sex, ignore.case = TRUE)]<-1
x$sex[grepl("^f", x$sex, ignore.case = TRUE)]<-2
x$class_section[x$class_section=="NA"]<-""
```

```{r main TB Dorm}
x$dorm_[!grepl("^B|^H|^G",x$dorm,ignore.case=TRUE)] <- ""
x$dorm[grepl("^H-",x$dorm,ignore.case=TRUE)] <- 1
x$dorm[grepl("^G",x$dorm,ignore.case=TRUE)] <- 3
x$dorm[grepl("^B",x$dorm,ignore.case=TRUE)] <- 2
x$dorm[grepl("^sta", x$dorm, ignore.case = TRUE)]<-5
x$dorm[grepl("^da", x$dorm, ignore.case = TRUE)]<-4
x$dorm[grepl("^mgh", x$dorm, ignore.case=TRUE)]<-6
x$dorm[grepl("^ygh", x$dorm, ignore.case=TRUE)]<-7
x$dorm[grepl("^sos", x$dorm, ignore.case=TRUE)]<-8
x$dorm[grepl("^ygy", x$dorm, ignore.case=TRUE)]<-10
x$dorm[grepl("^d/s", x$dorm, ignore.case=TRUE)]<-11
x$dorm[grepl("^s/c", x$dorm, ignore.case=TRUE)]<-12
x$dorm[grepl("^lgy", x$dorm, ignore.case=TRUE)]<-13
x$dorm[grepl("^sam", x$dorm, ignore.case=TRUE)]<-14
x$dorm[x$dorm==""]<-9
x$dorm[x$dorm=="NA"]<-99


x$enroll_date[x$enroll_date=="NA"]<-""

```

```{r occuapation}
x$occupation[x$occupation=="STUDENT"]<-1
x$occupation[x$occupation=="TEACHER"]<-2
x$occupation[x$occupation=="HEALTH-STAFF"]<-3
x$occupation[x$occupation=="HEALTH STAFF"]<-3
x$occupation[x$occupation=="OFFICE-STAFF"]<-4
x$occupation[x$occupation=="OFFICE STAFF"]<-4
x$occupation[x$occupation=="HOME-MOTHER"]<-5
x$occupation[x$occupation=="HOME MOTHER"]<-5
x$occupation[x$occupation=="MONK"]<-6
x$occupation[x$occupation=="NUN"]<-7
x$occupation[x$occupation=="COOK"]<-8
x$occupation[x$occupation=="DRIVER"]<-9
x$occupation[x$occupation=="HOME-FATHER"]<-10
x$occupation[x$occupation=="HOME FATHER"]<-10
x$occupation[x$occupation=="STAFF"]<-11
x$occupation[x$occupation=="OTHER"]<-11
x$occupation[x$occupation=="OTHER STAFF"]<-11
```

```{r Country}
x$birth_place[!grepl('^IND|^TIB|^NEP|^BHU|', x$birth_place,ignore.case=TRUE)] <- 5
x$birth_place[x$birth_place=="INDIA"]<-1
x$birth_place[x$birth_place=="TIBET"]<-2
x$birth_place[x$birth_place=="NEPAL"]<-3
x$birth_place[x$birth_place=="BHUTAN"]<-4
x$birth_place[x$birth_place=="USA"]<-5
x$birth_place[x$birth_place=="CANADA"]<-6


x$arrivalyear_fromtibet[x$arrivalyear_fromtibet=="NA"]<-""



x$ethnicity[x$ethnicity=="NA"]<-""
```


```{r run}
x$address_settlement_city[x$address_settlement_city=="NA"]<-""

x$weight_kg[x$weight_kg=="NA"]<-""
```


```{r export}
write.csv(x,"C:/Users/g_pun/Dropbox/ZeroTB/STCV/CONTACT_TRACE_clean.csv", na="")
```