---
title: "maindatabasetbinvestigation"
author: "Gopika Punchhi"
date: "12/11/2019"
output: html_document
---

This document only contains code for the tabs that are not contact trace, reactiv, or active tb (main database tabs)

Before running this document, change x=read.csv("LOCATION OF FILE TO READ IN", ......)
At the bottom of the document, change write.csv to the appropriate document name and location to save the new csv file for upload to REDCap

in the excel sheet, you need to assign the case designation variable to main databased investigation once you have converted to the new csv file using the code below
```{r institute, include=FALSE}
library(plyr)
library(readr)
library(dplyr)
library(tidyverse)
library(lubridate)
x=read.csv("C:/Users/g_pun/Dropbox/ZeroTB/STCV/CT_TST_REAC.csv",stringsAsFactors = FALSE, na.strings=TRUE)
##Insitute variable renaming
##need to write this in based on what you see in the document
x$institute[x$institute=="LTCV"]<-1
x$institute[x$institute=="LowerTCV"]<-1
x$institute[x$institute=="GTCV"]<-3
x$institute[x$institute=="TCV GOPUR"]<-3
x$institute[x$institute=="LTCV"]<-1
x$institute[x$institute=="LTCV"]<-1
x$institute[x$institute=="STSP"]<-10
x$institute[x$institute=="STCV"]<-4
```

```{r age}
x$age[x$age=="NA"]<-""
```

```{r sex}
x$sex[grepl("^m", x$sex, ignore.case = TRUE)]<-1
x$sex[grepl("^f", x$sex, ignore.case = TRUE)]<-2
x$class_section[x$class_section=="NA"]<-""
```

```{r main TB Dorm}
x$dorm_[!grepl("^B|^H|^G",x$dorm,ignore.case=TRUE)] <- ""
x$dorm[grepl("^H-",x$dorm,ignore.case=TRUE)] <- 1
x$dorm[grepl("^G",x$dorm,ignore.case=TRUE)] <- 3
x$dorm[grepl("^B",x$dorm,ignore.case=TRUE)] <- 2
x$dorm[grepl("^sta", x$dorm, ignore.case = TRUE)]<-5
x$dorm[grepl("^da", x$dorm, ignore.case = TRUE)]<-4
x$dorm[grepl("^mgh", x$dorm, ignore.case=TRUE)]<-6
x$dorm[grepl("^ygh", x$dorm, ignore.case=TRUE)]<-7
x$dorm[grepl("^sos", x$dorm, ignore.case=TRUE)]<-8
x$dorm[grepl("^ygy", x$dorm, ignore.case=TRUE)]<-10
x$dorm[grepl("^d/s", x$dorm, ignore.case=TRUE)]<-11
x$dorm[grepl("^s/c", x$dorm, ignore.case=TRUE)]<-12
x$dorm[grepl("^lgy", x$dorm, ignore.case=TRUE)]<-13
x$dorm[grepl("^sam", x$dorm, ignore.case=TRUE)]<-14
x$dorm[x$dorm==""]<-9
x$dorm[x$dorm=="NA"]<-99


x$enroll_date[x$enroll_date=="NA"]<-""

```

```{r occuapation}
x$occupation[x$occupation=="STUDENT"]<-1
x$occupation[x$occupation=="TEACHER"]<-2
x$occupation[x$occupation=="HEALTH-STAFF"]<-3
x$occupation[x$occupation=="HEALTH STAFF"]<-3
x$occupation[x$occupation=="OFFICE-STAFF"]<-4
x$occupation[x$occupation=="OFFICE STAFF"]<-4
x$occupation[x$occupation=="HOME-MOTHER"]<-5
x$occupation[x$occupation=="HOME MOTHER"]<-5
x$occupation[x$occupation=="MONK"]<-6
x$occupation[x$occupation=="NUN"]<-7
x$occupation[x$occupation=="COOK"]<-8
x$occupation[x$occupation=="DRIVER"]<-9
x$occupation[x$occupation=="HOME-FATHER"]<-10
x$occupation[x$occupation=="HOME FATHER"]<-10
x$occupation[x$occupation=="STAFF"]<-11
x$occupation[x$occupation=="OTHER"]<-11
x$occupation[x$occupation=="OTHER STAFF"]<-11
```

```{r Country}
x$birth_place[!grepl('^IND|^TIB|^NEP|^BHU|', x$birth_place,ignore.case=TRUE)] <- 5
x$birth_place[x$birth_place=="INDIA"]<-1
x$birth_place[x$birth_place=="TIBET"]<-2
x$birth_place[x$birth_place=="NEPAL"]<-3
x$birth_place[x$birth_place=="BHUTAN"]<-4
x$birth_place[x$birth_place=="USA"]<-5
x$birth_place[x$birth_place=="CANADA"]<-6


x$arrivalyear_fromtibet[x$arrivalyear_fromtibet=="NA"]<-""



x$ethnicity[x$ethnicity=="NA"]<-""
```


```{r run}
x$address_settlement_city[x$address_settlement_city=="NA"]<-""



x$weight_kg[x$weight_kg=="NA"]<-""
```

############################################################
ALL CODE ABOVE MUST BE RUN FOR EACH SHEET
############################################################




MAIN DATABASE tb INVESTIGATION CODE
```{r prev tb}
x$prev_tb[x$prev_tb=="NO"]<-0
x$prev_tb[x$prev_tb=="YES"]<-1
x$prev_tb[x$prev_tb=="UNKNOWN"]<-9
x$prev_tb[x$prev_tb=="NA"]<-99
```

```{r year of previous TB}
x$prevtb_year[x$prevtb_year=="NA"]<-99
x$prevtb_year[x$prevtb_year=="UNKNOWN"]<-9
```


```{r prev tb type}
x$prevtb_type[x$prevtb_type=="NON MDR"]<-0
x$prevtb_type[grepl("^no",x$prevtb_type, ignore.case = TRUE)]<-0
x$prevtb_type[x$prevtb_type=="MDR"]<-1
x$prevtb_type[grepl("^md",x$prevtb_type, ignore.case = TRUE)]<-1
x$prevtb_type[x$prevtb_type=="NA"]<-99
x$prevtb_type[x$prevtb_type=="UNKNOWN"]<-9

x$prevtb_site[x$prevtb_site=="UNKNOWN"]<-9
x$prevtb_site[x$prevtb_site=="NA"]<-99
```



```{r seizures}
x$seizures[x$seizures=="NO"]<-0
x$seizures[x$seizures=="no"]<-0
x$seizures[x$seizures=="YES"]<-1
x$seizures[x$seizures=="yes"]<-1
x$seizures[x$seizures=="UNKNOWN"]<-9
x$seizures[x$seizures=="NA"]<-99
```

```{r hepb}
x$hepb[x$hepb=="NO"]<-0
x$hepb[x$hepb=="YES"]<-1
x$hepb[x$hepb=="no"]<-0
x$hepb[x$hepb=="yes"]<-1
```

```{r preg_breastfeed}
x$preg_breastfeed[x$preg_breastfeed=="NO"]<-0
x$preg_breastfeed[x$preg_breastfeed=="PREG"]<-1
x$preg_breastfeed[grepl("^bre", x$preg_breastfeed, ignore.case = TRUE)]<-2
x$preg_breastfeed[x$preg_breastfeed=="BREASTFEED"]<-2
x$preg_breastfeed[x$preg_breastfeed=="UNKNOWN"]<-9
x$preg_breastfeed[x$preg_breastfeed=="NA"]<-99
```

```{r other comorbid}
x$other_cormorbid[grepl("^no", x$other_cormorbid, ignore.case = TRUE)]<-0
x$other_cormorbid[x$other_cormorbid=="DM"]<-1
x$other_cormorbid[x$other_cormorbid=="HTN"]<-2
x$other_cormorbid[x$other_cormorbid=="DM_HTN"]<-3
x$other_cormorbid[grepl("^o", x$other_cormorbid, ignore.case = TRUE)]<-4
x$other_cormorbid[x$other_cormorbid=="UNKNOWN"]<-9
x$other_cormorbid[x$other_cormorbid=="NA"]<-99
```

```{r longterm med}
x$longterm_med[x$longterm_med=="NONE"]<-0
x$longterm_med[x$longterm_med=="NO"]<-0
x$longterm_med[x$longterm_med=="ANTI-HEPB"]<-1
x$longterm_med[x$longterm_med=="ANTI HEPB"]<-1
x$longterm_med[x$longterm_med=="ANTI_SEIZURE"]<-2
x$longterm_med[x$longterm_med=="ANTI-SEIZURE"]<-2
x$longterm_med[x$longterm_med=="ANTI SEIZURE"]<-2
x$longterm_med[x$longterm_med=="ANTI_DM"]<-3
x$longterm_med[x$longterm_med=="ANTI-HTN"]<-4
x$longterm_med[x$longterm_med=="ANTI-DMHTN"]<-5
x$longterm_med[x$longterm_med=="ANTI-HEPBDM"]<-6
x$longterm_med[x$longterm_med=="ANTI-HEPHTN"]<-7
x$longterm_med[x$longterm_med=="ANTI-HEPBSEIZURE"]<-8
x$longterm_med[x$longterm_med=="ANTI-SEIZUREDM"]<-9
x$longterm_med[x$longterm_med=="ANTI_SEIZUREHTN"]<-10
x$longterm_med[x$longterm_med=="OTHER"]<-11
```

```{r eversmoked}
x$ever_smoked[x$ever_smoked=="NO"]<-0
x$ever_smoked[x$ever_smoked=="YES"]<-1
x$ever_smoked[x$ever_smoked=="UNKNOWN"]<-9
x$ever_smoked[x$ever_smoked=="NA"]<-99
```

```{r bcg tibetborn}
x$bcg_tibetborn[x$bcg_tibetborn=="NO"]<-0
x$bcg_tibetborn[x$bcg_tibetborn=="YES"]<-1
x$bcg_tibetborn[x$bcg_tibetborn=="UNKNOWN"]<-9
x$bcg_tibetborn[x$bcg_tibetborn=="NA"]<-99
```

```{r contact with TB in last two years}
x$contactsch_2yr[x$contactsch_2yr=="NO"]<-0
x$contactsch_2yr[x$contactsch_2yr=="YES"]<-1
x$contactsch_2yr[x$contactsch_2yr=="UNKNOWN"]<-9
x$contactsch_2yr[x$contactsch_2yr=="NA"]<-99
```

```{r drug sensitivity of Tb case at school}
x$indexcasesch_tbtype[x$indexcasesch_tbtype=="NON MDR"]<-0
x$indexcasesch_tbtype[x$indexcasesch_tbtype=="MDR"]<-1
x$indexcasesch_tbtype[x$indexcasesch_tbtype==""]<-""
x$indexcasesch_tbtype[x$indexcasesch_tbtype=="UNKNOWN"]<-9
x$indexcasesch_tbtype[x$indexcasesch_tbtype=="NA"]<-99
```

```{r index case at school}
x$indexcasesch_is[x$indexcasesch_is=="CLASS MATE"]<-1
x$indexcasesch_is[x$indexcasesch_is=="CLASS-MATE"]<-1
x$indexcasesch_is[x$indexcasesch_is=="CLASSMATE"]<-1
x$indexcasesch_is[x$indexcasesch_is=="DORM MATE"]<-2
x$indexcasesch_is[x$indexcasesch_is=="DORMMATE"]<-2
x$indexcasesch_is[x$indexcasesch_is=="DORM-MATE"]<-2
x$indexcasesch_is[x$indexcasesch_is=="CLASSDORM MATE"]<-3
x$indexcasesch_is[x$indexcasesch_is=="CLASS DORM MATE"]<-3
x$indexcasesch_is[x$indexcasesch_is=="CLASS DORM-MATE"]<-3
x$indexcasesch_is[x$indexcasesch_is=="SCHOOL STAFF"]<-4
x$indexcasesch_is[x$indexcasesch_is=="SCHOOL-STAFF"]<-4
x$indexcasesch_is[x$indexcasesch_is=="FRIEND"]<-5
x$indexcasesch_is[x$indexcasesch_is=="OTHER"]<-6
x$indexcasesch_is[x$indexcasesch_is=="NA"]<-99
x$indexcasesch_count[x$indexcasesch_count=="0"]<-0
x$indexcasesch_count[x$indexcasesch_count=="1"]<-1
x$indexcasesch_count[x$indexcasesch_count=="2"]<-2
x$indexcasesch_count[x$indexcasesch_count=="3"]<-3
x$indexcasesch_count[x$indexcasesch_count=="4"]<-3
x$indexcasesch_count[grepl("^>",x$indexcasesch_count, ignore.case=FALSE)]<-3
x$indexcasesch_count[x$indexcasesch_count=="NA"]<-99
```

```{r exposed to TB athome}
x$contacthome_2yr[x$contacthome_2yr=="NO"]<-0
x$contacthome_2yr[x$contacthome_2yr=="YES"]<-1
x$contacthome_2yr[x$contacthome_2yr=="UNKNOWN"]<-9
```

```{r drug sensitivity of the TB case at home}
x$indexcasehome_tbtype[x$indexcasehome_tbtype=="NON MDR"]<-0
x$indexcasehome_tbtype[x$indexcasehome_tbtype=="MDR"]<-1
x$indexcasehome_tbtype[x$indexcasehome_tbtype=="UNKNOWN"]<-9
x$indexcasehome_tbtype[x$indexcasehome_tbtype=="NA"]<-99
```

```{r index case at home}
x$indexcasehome_is[x$indexcasehome_is=="PARENT"]<-1
x$indexcasehome_is[x$indexcasehome_is=="SIBLING"]<-2
x$indexcasehome_is[x$indexcasehome_is=="GRANDPARENT"]<-3
x$indexcasehome_is[x$indexcasehome_is=="GRAND PARENT"]<-3
x$indexcasehome_is[x$indexcasehome_is=="OTHER"]<-4
x$indexcasehome_is[x$indexcasehome_is=="NA"]<-99
```

```{r indexcasehome_count}
x$indexcasehome_count[x$indexcasehome_count=="0"]<-0
x$indexcasehome_count[x$indexcasehome_count=="1"]<-1
x$indexcasehome_count[x$indexcasehome_count=="2"]<-2
x$indexcasehome_count[x$indexcasehome_count=="3"]<-3
x$indexcasehome_count[x$indexcasehome_count=="4"]<-3
x$indexcasehome_count[x$indexcasehome_count>="NA"]<-99
#### CHECK THIS LAST LINE OF CODE
```

```{r presence of cough}
x$cough[x$cough=="NO"]<-0
x$cough[x$cough=="YES"]<-1
```


```{r cough duration in weeks}
x$coughduration_wks[grepl("^l", x$coughduration_wks, ignore.case=TRUE)]<-1
x$coughduration_wks[grepl("^o", x$coughduration_wks, ignore.case=TRUE)]<-2
x$coughduration_wks[grepl("^t", x$coughduration_wks, ignore.case=TRUE)]<-3
x$coughduration_wks[grepl("^g", x$coughduration_wks, ignore.case=TRUE)]<-4
x$coughduration_wks[!grepl("^o|^t|^g", x$coughduration_wks, ignore.case=TRUE)]<-""
x$coughduration_wks[x$coughduration_wks=="NA"]<-99
```

```{r patient cough productive}
x$productive_cough[x$productive_cough=="NO"]<-0
x$productive_cough[x$productive_cough=="YES"]<-1
x$productive_cough[x$productive_cough=="NA"]<-99
```

```{r presence of blood in sputum}
x$blood_sputum[x$blood_sputum=="NO"]<-0
x$blood_sputum[x$blood_sputum=="YES"]<-1
x$blood_sputum[x$blood_sputum=="NA"]<-99
```

```{r fever}
x$fever[x$fever=="NO"]<-0
x$fever[x$fever=="YES"]<-1
```

```{r fever duration}
x$fever_duration[grepl("^l", x$fever_duration, ignore.case = TRUE)]<-1
x$fever_duration[grepl("^o", x$fever_duration, ignore.case = TRUE)]<-2
x$fever_duration[grepl("^g", x$fever_duration, ignore.case = TRUE)]<-3
x$fever_duration[!grepl("^l|^o|^g", x$fever_duration, ignore.case = TRUE)]<-""
x$fever_duration[x$fever_duration=="NA"]<-99
```

```{r presence of night sweats}
x$nightsweats_2wks[x$nightsweats_2wks=="NO"]<-0
x$nightsweats_2wks[x$nightsweats_2wks=="YES"]<-1
```

```{r weight loss in year prior}
x$wtloss_1month[x$wtloss_1month=="NO"]<-0
x$wtloss_1month[x$wtloss_1month=="YES"]<-1
```

```{r fatigue prior 2 weeks}
x$fatigue_last2wks[x$fatigue_last2wks=="NO"]<-0
x$fatigue_last2wks[x$fatigue_last2wks=="YES"]<-1
```

```{r ongoing chest pain}
x$chestpain_current[x$chestpain_current=="NO"]<-0
x$chestpain_current[x$chestpain_current=="YES"]<-1
```


```{r previous tst done}
x$tst1_done[x$tst1_done=="YES"]<-1
x$tst1_done[x$tst1_done=="PREV TB"]<-2
x$tst1_done[x$tst1_done=="PREVTB"]<-2
x$tst1_done[grepl("^pr", x$tst1_done, ignore.case=TRUE)]<-2
x$tst1_done[x$tst1_done=="NOT INDICATED"]<-3
x$tst1_done[x$tst1_done=="NOTINDICATED"]<-3
x$tst1_done[x$tst1_done=="NA"]<-99
x$tst1_done[x$tst1_done=="REFUSED"]<-4
x$tst1_date[x$tst1_date=="NA"]<-""
```

```{r main}
x$tst1_result[x$tst1_result=="NEGATIVE"]<-0
x$tst1_result[x$tst1_result=="POSITIVE"]<-1
x$tst1_result[x$tst1_result=="NOT DONE"]<-2
x$tst1_result[x$tst1_result=="UNKNOWN"]<-9

x$tst1_date_read[x$tst1_date_read=="NA"]<-""

x$tst1_adr[x$tst1_adr=="NONE"]<-0
x$tst1_adr[x$tst1_adr=="NO"]<-0
x$tst1_adr[x$tst1_adr=="YES"]<-1
x$tst1_adr[x$tst1_adr=="NOT DETECTED"]<-0
x$tst1_adr[x$tst1_adr=="DETECTED"]<-1
```


```{r wheal size}
x$wheal1_size[x$wheal1_size=="NA"]<-""
```

```{r date}
x$xpert1_date[x$xpert1_date=="NA"]<-""
```

```{r type of specimen xpert}
x$xpert1_specimen[x$xpert1_specimen=="SPUTUM"]<-1
x$xpert1_specimen[x$xpert1_specimen=="GA"]<-2
x$xpert1_specimen[grepl("^GA", x$xpert1_specimen, ignore.case = FALSE)]<-2
x$xpert1_specimen[x$xpert1_specimen=="PUS"]<-3
x$xpert1_specimen[x$xpert1_specimen=="PLEURAL FLUID"]<-4
x$xpert1_specimen[x$xpert1_specimen=="URINE"]<-5
x$xpert1_specimen[x$xpert1_specimen=="CSF"]<-6
x$xpert1_specimen[x$xpert1_specimen=="NA"]<-99
```

```{r result of xpert analysis}
x$xpert1_result[x$xpert1_result=="NOT DETECTED"]<-0
x$xpert1_result[x$xpert1_result=="NEGATIVE"]<-0
x$xpert1_result[x$xpert1_result=="DETECTED"]<-1
x$xpert1_result[x$xpert1_result=="POSITIVE"]<-1
x$xpert1_result[x$xpert1_result=="NA"]<-99
```

```{r drug sensitivty as per xpert analysis}
x$xpert1_mtb[x$xpert1_mtb=="VL"]<-0
x$xpert1_mtb[x$xpert1_mtb=="LOW"]<-1
x$xpert1_mtb[x$xpert1_mtb=="MED"]<-2
x$xpert1_mtb[x$xpert1_mtb=="HIGH"]<-3
x$xpert1_mtb[x$xpert1_mtb=="NA"]<-99
```

```{r rifampin resistance}
x$xpert1_rif[x$xpert1_rif=="SEN"]<-0
x$xpert1_rif[grepl("^s", x$xpert1_rif, ignore.case = TRUE)]<-0
x$xpert1_rif[x$xpert1_rif=="SENSITIVE"]<-0
x$xpert1_rif[x$xpert1_rif=="RES"]<-1
x$xpert1_rif[grepl("^r", x$xpert1_rif, ignore.case = TRUE)]<-1
x$xpert1_rif[x$xpert1_rif=="INDET"]<-2
x$xpert1_rif[grepl("^i", x$xpert1_rif, ignore.case = TRUE)]<-2
x$xpert1_rif[x$xpert1_rif=="NA"]<-99
```

```{r xpert2 date}
x$xpert2_date[x$xpert2_date=="NA"]<-""
```

```{r type of spec use for 2nd xpert}
x$xpert2_specimen[x$xpert2_specimen=="SPUTUM"]<-1
x$xpert2_specimen[x$xpert2_specimen=="GA"]<-2
x$xpert2_specimen[x$xpert2_specimen=="PUS"]<-3
x$xpert2_specimen[x$xpert2_specimen=="PLEURAL FLUID"]<-4
x$xpert2_specimen[x$xpert2_specimen=="URINE"]<-5
x$xpert2_specimen[x$xpert2_specimen=="CSF"]<-6
x$xpert2_specimen[x$xpert2_specimen=="NA"]<-99
x$xpert2_specimen[x$xpert2_specimen=="YES"]<-7
```

```{r result of xpert2}
x$xpert2_result[x$xpert2_result=="NOT DETECTED"]<-0
x$xpert2_result[x$xpert2_result=="NEGATIVE"]<-0
x$xpert2_result[x$xpert2_result=="DETECTED"]<-1
x$xpert2_result[x$xpert2_result=="POSITIVE"]<-1
x$xpert2_result[x$xpert2_result=="NA"]<-99
x$xpert2_result[x$xpert2_result=="ABNORMAL"]<-2
x$xpert2_result[x$xpert2_result=="NORMAL"]<-3
```


```{r drug sensitivty as per xpert2 analysis}
x$xpert2_mtb[x$xpert2_mtb=="VL"]<-0
x$xpert2_mtb[x$xpert2_mtb=="LOW"]<-1
x$xpert2_mtb[x$xpert2_mtb=="MED"]<-2
x$xpert2_mtb[x$xpert2_mtb=="HIGH"]<-3
x$xpert2_mtb[x$xpert2_mtb=="NA"]<-99
```

```{r rifampin resistance 2}
x$xpert2_rif[x$xpert2_rif=="SEN"]<-0
x$xpert2_rif[grepl("^s", x$xpert2_rif, ignore.case = TRUE)]<-0
x$xpert2_rif[x$xpert2_rif=="SENSITIVE"]<-0
x$xpert2_rif[x$xpert2_rif=="RES"]<-1
x$xpert2_rif[grepl("^r", x$xpert2_rif, ignore.case = TRUE)]<-1
x$xpert2_rif[x$xpert2_rif=="INDET"]<-2
x$xpert2_rif[grepl("^i", x$xpert2_rif, ignore.case = TRUE)]<-2
x$xpert2_rif[x$xpert2_rif=="NA"]<-99
```

```{r cxr}
x$cxr[x$cxr=="NA"]<-99
x$cxr[x$cxr=="YES"]<-1
x$cxr[x$cxr=="NO"]<-0
```

```{r cxr result}
x$cxr_result[x$cxr_result=="NORMAL"]<-0
x$cxr_result[x$cxr_result=="ABNORMAL"]<-1
x$cxr_result[x$cxr_result=="NA"]<-99
```

```{r diagnosed with active TB}
x$tb_diagnosed[x$tb_diagnosed=="NO"]<-0
x$tb_diagnosed[x$tb_diagnosed=="YES"]<-1
x$tb_diagnosed[x$tb_diagnosed=="NA"]<-99
```

```{r total num of students}
x$total_students[x$total_students=="NA"]<-""
x$total_staff[x$total_staff=="NA"]<-""
```

```{r total staff}
x$total_monks_nuns[x$total_monks_nuns=="NA"]<-""
```

```{r notes main}
x$notes_main[x$notes_main=="NA"]<-""
x$notes[x$notes=="NA"]<-""
```

```{r complete}
x$main_database_demographics_complete<-2
x$main_database_tbinvestigation_complete<-2
x$active_tb_tbinvestigation_complete<-2
x$tst_reactive_treatment_complete<-2
```

```{r export}
write.csv(x,"C:/Users/g_pun/Dropbox/ZeroTB/STCV/CONTACT_TRACE_clean.csv", na="")
```