---
title: "reactive"
author: "Gopika Punchhi"
date: "12/11/2019"
output: html_document
---

This document only contain code for the reactve (tst or st tst tabs) 

Before running this document, change x=read.csv("LOCATION OF FILE TO READ IN", ......)
At the bottom of the document, change write.csv to the appropriate document name and location to save the new csv file for upload to REDCap

in the excel sheet, you need to assign the case designation variable to the correct reactuve designation once you have converted to the new csv file using the code below

```{r institute, include=FALSE}
library(plyr)
library(readr)
library(dplyr)
library(tidyverse)
library(lubridate)
x=read.csv("C:/Users/g_pun/Dropbox/ZeroTB/STCV/CT_TST_REAC.csv",stringsAsFactors = FALSE, na.strings=TRUE)
##Insitute variable renaming
##need to write this in based on what you see in the document
x$institute[x$institute=="LTCV"]<-1
x$institute[x$institute=="LowerTCV"]<-1
x$institute[x$institute=="GTCV"]<-3
x$institute[x$institute=="TCV GOPUR"]<-3
x$institute[x$institute=="LTCV"]<-1
x$institute[x$institute=="LTCV"]<-1
x$institute[x$institute=="STSP"]<-10
x$institute[x$institute=="STCV"]<-4
```

```{r age}
x$age[x$age=="NA"]<-""
```

```{r sex}
x$sex[grepl("^m", x$sex, ignore.case = TRUE)]<-1
x$sex[grepl("^f", x$sex, ignore.case = TRUE)]<-2
x$class_section[x$class_section=="NA"]<-""
```

```{r main TB Dorm}
x$dorm_[!grepl("^B|^H|^G",x$dorm,ignore.case=TRUE)] <- ""
x$dorm[grepl("^H-",x$dorm,ignore.case=TRUE)] <- 1
x$dorm[grepl("^G",x$dorm,ignore.case=TRUE)] <- 3
x$dorm[grepl("^B",x$dorm,ignore.case=TRUE)] <- 2
x$dorm[grepl("^sta", x$dorm, ignore.case = TRUE)]<-5
x$dorm[grepl("^da", x$dorm, ignore.case = TRUE)]<-4
x$dorm[grepl("^mgh", x$dorm, ignore.case=TRUE)]<-6
x$dorm[grepl("^ygh", x$dorm, ignore.case=TRUE)]<-7
x$dorm[grepl("^sos", x$dorm, ignore.case=TRUE)]<-8
x$dorm[grepl("^ygy", x$dorm, ignore.case=TRUE)]<-10
x$dorm[grepl("^d/s", x$dorm, ignore.case=TRUE)]<-11
x$dorm[grepl("^s/c", x$dorm, ignore.case=TRUE)]<-12
x$dorm[grepl("^lgy", x$dorm, ignore.case=TRUE)]<-13
x$dorm[grepl("^sam", x$dorm, ignore.case=TRUE)]<-14
x$dorm[x$dorm==""]<-9
x$dorm[x$dorm=="NA"]<-99


x$enroll_date[x$enroll_date=="NA"]<-""

```

```{r occuapation}
x$occupation[x$occupation=="STUDENT"]<-1
x$occupation[x$occupation=="TEACHER"]<-2
x$occupation[x$occupation=="HEALTH-STAFF"]<-3
x$occupation[x$occupation=="HEALTH STAFF"]<-3
x$occupation[x$occupation=="OFFICE-STAFF"]<-4
x$occupation[x$occupation=="OFFICE STAFF"]<-4
x$occupation[x$occupation=="HOME-MOTHER"]<-5
x$occupation[x$occupation=="HOME MOTHER"]<-5
x$occupation[x$occupation=="MONK"]<-6
x$occupation[x$occupation=="NUN"]<-7
x$occupation[x$occupation=="COOK"]<-8
x$occupation[x$occupation=="DRIVER"]<-9
x$occupation[x$occupation=="HOME-FATHER"]<-10
x$occupation[x$occupation=="HOME FATHER"]<-10
x$occupation[x$occupation=="STAFF"]<-11
x$occupation[x$occupation=="OTHER"]<-11
x$occupation[x$occupation=="OTHER STAFF"]<-11
```

```{r Country}
x$birth_place[!grepl('^IND|^TIB|^NEP|^BHU|', x$birth_place,ignore.case=TRUE)] <- 5
x$birth_place[x$birth_place=="INDIA"]<-1
x$birth_place[x$birth_place=="TIBET"]<-2
x$birth_place[x$birth_place=="NEPAL"]<-3
x$birth_place[x$birth_place=="BHUTAN"]<-4
x$birth_place[x$birth_place=="USA"]<-5
x$birth_place[x$birth_place=="CANADA"]<-6


x$arrivalyear_fromtibet[x$arrivalyear_fromtibet=="NA"]<-""



x$ethnicity[x$ethnicity=="NA"]<-""
```


```{r run}
x$address_settlement_city[x$address_settlement_city=="NA"]<-""



x$weight_kg[x$weight_kg=="NA"]<-""
```

```{r reactive TB}
x$prev_therapy[grepl("NA",x$prev_therapy,ignore.case=TRUE)]<-""
x$prev_therapy[grepl("RECE",x$prev_therapy,ignore.case=TRUE)]<-1
x$prev_therapy[grepl("^NOT RECE",x$prev_therapy,ignore.case=TRUE)]<-2
x$prev_therapy[grepl("^C",x$prev_therapy,ignore.case=TRUE)]<-3
x$prev_therapy[grepl("^NOT RE",x$prev_therapy,ignore.case=TRUE)]<-5
x$prev_therapy[grepl("^A",x$prev_therapy,ignore.case=TRUE)]<-6
x$prev_therapy[grepl("^TB",x$prev_therapy,ignore.case=TRUE)]<-6

x$prev_ther_no[x$prev_ther_no=="NA"]<-""

x$prev_therapy_reg[grepl("NA",x$prev_therapy_reg,ignore.case=TRUE)]<-""
x$prev_therapy_reg[grepl("4R",x$prev_therapy_reg,ignore.case=TRUE)]<-1
x$prev_therapy_reg[grepl("3HR",x$prev_therapy_reg,ignore.case=TRUE)]<-2
x$prev_therapy_reg[grepl("6H",x$prev_therapy_reg,ignore.case=TRUE)]<-3
x$prev_therapy_reg[grepl("3HP",x$prev_therapy_reg,ignore.case=TRUE)]<-4
x$prev_therapy_reg[grepl("NA",x$prev_therapy_reg,ignore.case=TRUE)]<-99

x$prevther_startdate[x$prevther_startdate=="NA"]<-""

x$prevther_adr[grepl("NA",x$prevther_adr,ignore.case=TRUE)]<-99
x$prevther_adr[grepl("^N",x$prevther_adr,ignore.case=TRUE)]<-0
x$prevther_adr[grepl("^Y",x$prevther_adr,ignore.case=TRUE)]<-1

x$typeofadr[x$typeofadr=="NA"]<-""

x$culprit_drug[grepl("NA",x$culprit_drug ,ignore.case=TRUE)]<-99
x$culprit_drug[grepl("Rif",x$culprit_drug,ignore.case=TRUE)]<-1
x$culprit_drug[grepl("^I",x$culprit_drug,ignore.case=TRUE)]<-2
x$culprit_drug[grepl("Rif-Inh",x$culprit_drug,ignore.case=TRUE)]<-3

x$ptsa_gi[x$ptsa_gi=="NO"]<-0
x$ptsa_gi[x$ptsa_gi=="YES"]<-1
x$ptsa_gi[x$ptsa_gi=="NA"]<-99

x$ptsa_red[x$ptsa_red=="NO"]<-0
x$ptsa_red[x$ptsa_red=="YES"]<-1
x$ptsa_red[x$ptsa_red=="NA"]<-99

x$ptsa_sleep[x$ptsa_sleep=="NO"]<-0
x$ptsa_sleep[x$ptsa_sleep=="YES"]<-1
x$ptsa_sleep[x$ptsa_sleep=="NA"]<-99

x$ptsa_head[x$ptsa_head=="NO"]<-0
x$ptsa_head[x$ptsa_head=="YES"]<-1
x$ptsa_head[x$ptsa_head=="NA"]<-99

x$ptsa_jaundice[x$ptsa_jaundice=="NO"]<-0
x$ptsa_jaundice[x$ptsa_jaundice=="YES"]<-1
x$ptsa_jaundice[x$ptsa_jaundice=="NA"]<-99

x$ptsa_rash[x$ptsa_rash=="NO"]<-0
x$ptsa_rash[x$ptsa_rash=="YES"]<-1
x$ptsa_rash[x$ptsa_rash=="NA"]<-99

x$ptsa_hepa[x$ptsa_hepa=="NO"]<-0
x$ptsa_hepa[x$ptsa_hepa=="YES"]<-1
x$ptsa_hepa[x$ptsa_hepa=="NA"]<-99

x$totalbil_1[grepl("NA",x$totalbil_1 ,ignore.case=TRUE)]<-""

x$directl_1[grepl("NA",x$directl_1,ignore.case=TRUE)]<-""

x$sgpt_1[grepl("NA",x$sgpt_1,ignore.case=TRUE)]<-""
x$sgot_1[grepl("NA",x$sgot_1,ignore.case=TRUE)]<-""

x$totalbil_2[grepl("NA",x$totalbil_2,ignore.case=TRUE)]<-""

x$directbil_2[grepl("NA", x$directbil_2,ignore.case=TRUE)]<-""

x$sgpt_2[grepl("NA",x$sgpt_2,ignore.case=TRUE)]<-""
x$sgot_2[grepl( "NA",x$sgot_2,ignore.case=TRUE)]<-""

x$totalbil_3[grepl("NA",x$totalbil_3,ignore.case=TRUE)]<-""

x$directbil_3[grepl("NA",x$directbil_3,ignore.case=TRUE)]<-""

x$sgpt_3[grepl("NA",x$sgpt_3,ignore.case=TRUE)]<-""
x$sgot_3[grepl("NA",x$sgot_3,ignore.case=TRUE)]<-""

x$totalbil_4[grepl("NA",x$totalbil_4,ignore.case=TRUE)]<-""

x$directbil_4[grepl("NA",x$directbil_4,ignore.case=TRUE)]<-""

x$sgpt_4[grepl("NA",x$sgpt_4,ignore.case=TRUE)]<-""
x$sgot_4[grepl("NA",x$sgot_4,ignore.case=TRUE)]<-"" 

x$prevtherapy_held[grepl("NA",x$prevtherapy_held,ignore.case=TRUE)]<-99
x$prevtherapy_held[grepl("^N",x$prevtherapy_held,ignore.case=TRUE)]<-0
x$prevtherapy_held[grepl("^Y",x$prevtherapy_held,ignore.case=TRUE)]<-1

x$date_prevther_held[x$date_prevther_held=="NA"]<-""
x$date_prevther_restarted[x$date_prevther_restarted=="NA"]<-""

x$prev_therapy_revised[grepl("NA",x$prev_therapy_revised,ignore.case=TRUE)]<-99
x$prev_therapy_revised[grepl("^N",x$prev_therapy_revised,ignore.case=TRUE)]<-0
x$prev_therapy_revised[grepl("^Y",x$prev_therapy_revised,ignore.case=TRUE)]<-1

x$revised_prevther_reg[grepl("NA",x$revised_prevther_reg,ignore.case=TRUE)]<-""
x$revised_prevther_reg[grepl("^4",x$revised_prevther_reg,ignore.case=TRUE)]<-1
x$revised_prevther_reg[grepl("^3HR",x$revised_prevther_reg,ignore.case=TRUE)]<-2
x$revised_prevther_reg[grepl("^6",x$revised_prevther_reg,ignore.case=TRUE)]<-3
x$revised_prevther_reg[grepl("^3HP",x$revised_prevther_reg,ignore.case=TRUE)]<-4
x$revised_prevther_reg[!grepl("^4|^3HR|^6|^3HP|^NA", x$revised_prevther_reg,ignore.case=TRUE)]<- ""

x$prevther_outcome[grepl("NA",x$prevther_outcome,ignore.case=TRUE)]<-""
x$prevther_outcome[grepl("^COM",x$prevther_outcome,ignore.case=TRUE)]<-1
x$prevther_outcome[grepl("^L",x$prevther_outcome,ignore.case=TRUE)]<-2
x$prevther_outcome[grepl("^A",x$prevther_outcome,ignore.case=TRUE)]<-3
x$prevther_outcome[grepl("TB",x$prevther_outcome,ignore.case=TRUE)]<-3
x$prevther_outcome[!grepl("NA|^COM|^L|^A|TB", x$prevther_outcome,ignore.case=TRUE)]<- 4

x$if_other_specify[x$if_other_specify=="NA"]<-""

x$prevther_stopped_premature[grepl("NA",x$prevther_stopped_premature,ignore.case=TRUE)]<-99
x$prevther_stopped_premature[grepl("^N",x$prevther_stopped_premature,ignore.case=TRUE)]<-0
x$prevther_stopped_premature[grepl("^Y",x$prevther_stopped_premature,ignore.case=TRUE)]<-1

x$prevther_stopped_reason[grepl("NA",x$prevther_stopped_reason,ignore.case=TRUE)]<-99
x$prevther_stopped_reason[grepl("^H",x$prevther_stopped_reason,ignore.case=TRUE)]<- 1
x$prevther_stopped_reason[grepl("^other tox",x$prevther_stopped_reason,ignore.case=TRUE)]<- 2
x$prevther_stopped_reason[grepl("^discont",x$prevther_stopped_reason,ignore.case=TRUE)]<- 3
x$prevther_stopped_reason[!grepl("^H|^other tox|^discont", x$prevther_stopped_reason,ignore.case=TRUE)]<- 4

x$tst_reactive_treatment_complete[x$tst_reactive_treatment_complete=="INCOMPLETE"]<-0
x$tst_reactive_treatment_complete[x$tst_reactive_treatment_complete=="UNVERIFIED"]<-1
x$tst_reactive_treatment_complete[x$tst_reactive_treatment_complete=="COMPLETE"]<-2

x$prevther_startdate[grepl("NA",x$prevther_startdate,ignore.case=TRUE)]<-""

x$date_prevther_held[grepl("NA",x$date_prevther_held,ignore.case=TRUE)]<-""
x$date_prevther_restarted[grepl("NA",x$date_prevther_restarted,ignore.case=TRUE)]<-""

x$date_rx_start = mdy(x$date_rx_start)
x$date_rx_stopped = mdy(x$date_rx_stopped)

x$main_database_demographics_complete<-2
x$main_database_tbinvestigation_complete<-2
x$active_tb_tbinvestigation_complete<-2
x$tst_reactive_treatment_complete<-2
```


```{r export}
write.csv(x,"C:/Users/g_pun/Dropbox/ZeroTB/STCV/CONTACT_TRACE_clean.csv", na="")
```